---
title: "ARMA-X Figures"
output:
  pdf_document: 
    toc: true
    fig_caption: yes
    latex_engine: lualatex
header-includes:
  - \usepackage{amsmath}
---
\newpage

```{r library_setup, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
rm(list=ls())
require(tinytex) #LaTeX
require(ggplot2) #plots
require(AEC) #JP-Renne functions
require(AER) #NW formula
require(forecast) #time series stuff
require(expm) #matrix exponents
require(here) #directory finder
require(stringr) # analysis of strings, important for the detection in tweets
require(dplyr) #data management
require(lubridate) #data dates management
require(zoo) #for lagging
require(jtools) #tables
require(huxtable) #tables
require(lmtest) #reg tests
require(vroom) #for loading data
require(data.table) #for data filtering
require(sysid) #for ARMA-X modeling
require(sandwich) #regression errors
require(stargazer) #nice reg tables
require(tidytext) #text mining
require(textstem) #lemmatization
require(quanteda) #tokenization
require(texreg) #arima tables
require(future.apply) #parallel computation (speed)
require(aTSA) #adf test

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
source(here("helperfunctions/truths_cleaning_function.R"))
source(here("helperfunctions/armax_functions.R"))

```


# Full Timeframe (Jan 2024 to May 2025)

```{r datasetup, results=FALSE, warning=FALSE, message=FALSE}

#load final dataset
source(here("helperfunctions/full_data.R"))

#backup
backup = data

#select timeframe 
data = filter(data,between(timestamp, as.Date('2014-01-01'), as.Date('2025-05-07')))

```


## SPY Models

We choose the specification in the armax_models file. In this file, we will
just run said specifications to produce nice tables and graphs to include in 
our final paper. This is also why there are specification differences in the 
separate timeframes. We always use the best fit we found earlier.


```{r fitting models, results=F, warning=F, message=F}

models <- list()

# ARMA-X(3,3,1) with Tweet Dummy as Exogenous
models[["Model 1"]] <- armax(data$SPY_vol, xreg = data$dummy, latex = F,
                             nb.lags = 1, p = 3, q = 3) 

# ARMA-X(3,3,1) with Tweet Count as Exogenous
models[["Model 2"]] <- armax(data$SPY_vol, xreg = data$N, latex = F,
                             nb.lags = 1, p = 3, q = 3) 

# ARMA-X(3,2,3) with Tariff Mentions as Exogenous
models[["Model 3"]] <- armax(data$SPY_vol, xreg = data$tariff, latex = F,
                             nb.lags = 3, p = 3, q = 2) 

# ARMA-X(3,2,1) with Trade Mentions as Exogenous
models[["Model 4"]] <- armax(data$SPY_vol, xreg = data$trade, latex = F,
                             nb.lags = 1, p = 3, q = 2) 

# ARMA-X(3,2,0) with China Mentions as Exogenous
models[["Model 5"]] <- armax(data$SPY_vol, xreg = data$china, latex = F,
                             nb.lags = 0, p = 3, q = 2) 

```

## SPY Table

```{r creating table, results="asis", warning=F, message=F}

names = list( "ar1" = "AR(1)",
              "ar2" = "AR(2)",
              "ar3" = "AR(3)",
              "ma1" = "MA(1)",
              "ma2" = "MA(2)",
              "ma3" = "MA(3)",
              "(Intercept)" = "Constant",
              "dummy_lag_0" = "$TweetDummy_{t}$",
              "dummy_lag_1" = "$TweetDummy_{t-1}$",
              "N_lag_0" = "$TweetCount_{t}$",
              "N_lag_1" = "$TweetCount_{t-1}$",
              "tariff_lag_0" = "$Tariff_{t}$",
              "tariff_lag_1" = "$Tariff_{t-1}$",
              "tariff_lag_2" = "$Tariff_{t-2}$",
              "tariff_lag_3" = "$Tariff_{t-3}$",
              "trade_lag_0" = "$Trade_{t}$",
              "trade_lag_1" = "$Trade_{t-1}$",
              "china_lag_0" = "$China_{t}$")

texreg(models,
          custom.model.names = names(models), 
          custom.coef.map = names,
          caption = "ARMAX Models of Average Hourly Volatility",
          caption.above = TRUE,
          label = "tab:armax",
          digits = 4)

```


## SPY IRFs

```{r SPYirf, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(models[["Model 1"]],nb.periods,title="Tweet Dummy Shock")
irf.plot(models[["Model 2"]],nb.periods,title="Tweet Count Shock")
irf.plot(models[["Model 3"]],nb.periods,title="Tariff Mention Shock")
irf.plot(models[["Model 4"]],nb.periods,title="Trade Mention Shock")
irf.plot(models[["Model 5"]],nb.periods,title="China Mention Shock")

```


## SPY Residuals
```{r SPYresiduals, warning=F, message=F, results=F}

res1 = checkresiduals(models[["Model 1"]], plot = FALSE)
res2 = checkresiduals(models[["Model 2"]], plot = FALSE)
res3 = checkresiduals(models[["Model 3"]], plot = FALSE)
res4 = checkresiduals(models[["Model 4"]], plot = FALSE)
res5 = checkresiduals(models[["Model 5"]], plot = FALSE)

```

```{r SPYresiduals table, warning=F, message=F}

resnames = c("Twitter Dummy", "Twitter Count", "Tariff", "Trade", "China")

#extract p-values directly from checkresiduals results
pvals <- data.frame(Model = resnames,
                    `Ljung-Box p-value` = c(
                      res1$p.value,
                      res2$p.value,
                      res3$p.value,
                      res4$p.value,
                      res5$p.value))

#table
knitr::kable(pvals, digits = 100, caption = "Full Timeframe Ljung-Box Test p-values")

```



# First Term

```{r datasetup first, results=FALSE, warning=FALSE, message=FALSE}

#load final dataset
data = backup

#first term
data = filter(data,between(timestamp, as.Date('2017-01-20'), as.Date('2021-01-20')))

```

## SPY Models

```{r 1st term models, results=F, warning=F, message=F}

models <- list()

# ARMA-X(3,3,0) with Tariff Mentions as Exogenous
models[["First Term (1)"]] <- armax(data$SPY_vol, xreg = data$tariff, latex = F,
                             nb.lags = 0, p = 3, q = 3) 

# ARMA-X(3,3,0) with Trade Mentions as Exogenous
models[["First Term (2)"]] <- armax(data$SPY_vol, xreg = data$trade, latex = F,
                             nb.lags = 0, p = 3, q = 3)

# ARMA-X(3,3,0) with Trade Mentions as Exogenous
models[["First Term (3)"]] <- armax(data$SPY_vol, xreg = data$china, latex = F,
                             nb.lags = 0, p = 3, q = 3) 

```


## SPY Residuals
```{r 1st SPYresiduals, warning=F, message=F, results=F}

res6 = checkresiduals(models[["First Term (1)"]], plot = FALSE)
res7 = checkresiduals(models[["First Term (2)"]], plot = FALSE)
res8 = checkresiduals(models[["First Term (3)"]], plot = FALSE)

pvals_new1 <- data.frame(
  Model = c("First Term Tariffs", "First Term Trade", "First Term China"),
  `Ljung-Box p-value` = c(
    res6$p.value,
    res7$p.value,
    res8$p.value))

```



# Second Term

```{r datasetup second, results=FALSE, warning=FALSE, message=FALSE}

#load final dataset
data = backup

#second term
data = filter(data,between(timestamp, as.Date('2025-01-20'), as.Date('2025-05-07')))

```

## SPY Models

```{r 2nd term models, results=F, warning=F, message=F}

# ARMA-X(3,2,3) with Tariff Mentions as Exogenous
models[["Second Term (1)"]] <- armax(data$SPY_vol, xreg = data$tariff, latex = F,
                             nb.lags = 2, p = 1, q = 2) 

# ARMA-X(3,2,1) with Trade Mentions as Exogenous
models[["Second Term (2)"]] <- armax(data$SPY_vol, xreg = data$trade, latex = F,
                             nb.lags = 0, p = 1, q = 2) 

# ARMA-X(3,2,0) with China Mentions as Exogenous
models[["Second Term (3)"]] <- armax(data$SPY_vol, xreg = data$china, latex = F,
                             nb.lags = 2, p = 1, q = 2) 

```


## SPY IRFs
```{r 2nd SPYirf, warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(models[["Second Term (1)"]],nb.periods,title="Tariff Mention Shock")
irf.plot(models[["Second Term (3)"]],nb.periods,title="China Mention Shock")

```


## SPY Residuals
```{r 2nd SPYresiduals, results=F, warning=F, message=F}

res9 = checkresiduals(models[["Second Term (1)"]], plot = FALSE)
res10 = checkresiduals(models[["Second Term (2)"]], plot = FALSE)
res11 = checkresiduals(models[["Second Term (3)"]], plot = FALSE)

pvals_new2 <- data.frame(
  Model = c("Second Term Tariffs", "Second Term Trade", "Second Term China"),
  `Ljung-Box p-value` = c(
    res9$p.value,
    res10$p.value,
    res11$p.value))

#combine with other term
pvals_combined <- rbind(pvals_new1, pvals_new2)

```


## SPY Table (both terms)

\centering
```{r table with separate terms, results="asis", warning=F, message=F}

xnames = list("ar1" = "AR(1)",
              "ar2" = "AR(2)",
              "ar3" = "AR(3)",
              "ma1" = "MA(1)",
              "ma2" = "MA(2)",
              "ma3" = "MA(3)",
              "(Intercept)" = "Constant",
              "tariff_lag_0" = "$Tariff_{t}$",
              "tariff_lag_1" = "$Tariff_{t-1}$",
              "tariff_lag_2" = "$Tariff_{t-2}$",
              "trade_lag_0" = "$Trade_{t}$",
              "china_lag_0" = "$China_{t}$",
              "china_lag_1" = "$China_{t-1}$",
              "china_lag_2" = "$China_{t-2}$")

texreg(models,
       custom.model.names = names(models), 
       custom.coef.map = xnames,
       caption = "Split-Term ARMAX Models of Average Hourly Volatility",
       caption.above = TRUE,
       label = "tab:armax_term",
       digits = 4)

```


## SPY Residuals Table (both terms)
```{r resterms table, message=FALSE, warning=FALSE}

knitr::kable(pvals_combined, digits = 100, caption = "Separate Terms Ljung-Box Test p-values")

```




