---
title: "ARMA-X Analysis"
output:
  pdf_document: 
    toc: true
    fig_caption: yes
    latex_engine: lualatex
header-includes:
  - \usepackage{amsmath}
---
\newpage

```{r library_setup, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
rm(list=ls())
require(tinytex) #LaTeX
require(ggplot2) #plots
require(AEC) #JP-Renne functions
require(AER) #NW formula
require(forecast) #time series stuff
require(expm) #matrix exponents
require(here) #directory finder
require(stringr) # analysis of strings, important for the detection in tweets
require(dplyr) #data management
require(lubridate) #data dates management
require(zoo) #for lagging
require(jtools) #tables
require(huxtable) #tables
require(lmtest) #reg tests
require(vroom) #for loading data
require(data.table) #for data filtering
require(sysid) #for ARMA-X modeling
require(sandwhich) #regression errors
require(stargazer) #nice reg tables
require(tidytext) #text mining
require(textstem) #lemmatization
require(quanteda) #tokenization
require(texreg) #arima tables

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
source(here("helperfunctions/truths_cleaning_function.R"))
source(here("helperfunctions/armax_functions.R"))
```


# Data 


## Load Base Data

```{r data_setup, results=FALSE, warning=FALSE, message=FALSE}

# 1. Load Political Social Media

#contains posts from Twitter & TruthSocial
social <- read.csv(here("data/mothership", "social.csv"))

social_hourly <- read.csv(here("data/mothership", "socialhourly.csv"))


# 2. Load Financial

#S&P500
SPY <- read.csv(here("data/mothership", "SPY.csv"))

#STOXX50
VGK <- read.csv(here("data/mothership", "VGK.csv"))

#CSI 300 (China)
ASHR <- read.csv(here("data/mothership", "ASHR.CSV"))

```

```{r data_time, results=FALSE, warning=FALSE, message=FALSE}

#make posixct
SPY$timestamp = as.POSIXct(SPY$timestamp,format = "%Y-%m-%d %H:%M:%S")
VGK$timestamp = as.POSIXct(VGK$timestamp,format = "%Y-%m-%d %H:%M:%S")
ASHR$timestamp = as.POSIXct(ASHR$timestamp,format = "%Y-%m-%d %H:%M:%S")
social$timestamp = as.POSIXct(social$timestamp,format = "%Y-%m-%d %H:%M:%S")
social_hourly$timestamp = as.POSIXct(social_hourly$timestamp,format = "%Y-%m-%d %H:%M:%S")

```



## Volatility
```{r volatility}

#find hourly volatility
#NOTE: this ignores tweets made outside trading hours!!
SPY_volatility_alltime = dplyr::select(SPY,timestamp,r_vol_h)

#aggregating per hour
SPY_volatility_alltime = SPY_volatility_alltime %>%
          mutate(timestamp = floor_date(timestamp, unit = "hour")) %>%
          distinct(timestamp, .keep_all = TRUE) 
   
#select time period
SPY_volatility = filter(SPY_volatility_alltime,
                  between(timestamp, 
                          as.Date('2013-01-01'), 
                          as.Date('2025-04-10')))


```

## Number of Posts 
```{r social media count}

#find count
tweetcount_alltime = dplyr::select(social_hourly,timestamp,N)

#select time period
tweetcount = filter(tweetcount_alltime,
                  between(timestamp, 
                          as.Date('2013-01-01'), 
                          as.Date('2025-04-10')))

#plot
ggplot(tweetcount_alltime, aes(x = timestamp, y = N)) +
    geom_point(color = "#253494", size = 1) +
    scale_x_datetime(date_labels = "%b %Y", date_breaks = "9 month") +
    labs(title = "Trump Social Media Count",
         x = NULL,
         y = "number of tweets/truths") +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.title = element_text(face = "bold", hjust = 0.5))
```

## Dummy for Social Media Post
```{r dummy}

#find dummy
tweetdummy_alltime = dplyr::select(social_hourly,timestamp,dummy)

#select time period
tweetdummy = filter(tweetdummy_alltime,
                  between(timestamp, 
                          as.Date('2013-01-01'), 
                          as.Date('2025-04-10')))

```

## Number of Tweets Mentioning Tariffs 
```{r tariff}

#find count
tariff_alltime = dplyr::select(social_hourly,timestamp,total_tariff)

#select time period
tariff = filter(tariff_alltime,
                  between(timestamp, 
                          as.Date('2013-01-01'), 
                          as.Date('2025-04-10')))

```

## Number of Tweets Mentioning Trade 
```{r trade}

#find count
trade_alltime = dplyr::select(social_hourly,timestamp,total_trade)

#select time period
trade = filter(trade_alltime,
                  between(timestamp, 
                          as.Date('2013-01-01'), 
                          as.Date('2025-04-10')))

```

## Proportion of Positive 
```{r positive}

#find count
positive_alltime = dplyr::select(social_hourly,timestamp,prop_positive)

#select time period
positive = filter(positive_alltime,
                  between(timestamp, 
                          as.Date('2013-01-01'), 
                          as.Date('2025-04-10')))

```

## Proportion of Negative 
```{r positive}

#find count
negative_alltime = dplyr::select(social_hourly,timestamp,prop_negative)

#select time period
negative = filter(negative_alltime,
                  between(timestamp, 
                          as.Date('2013-01-01'), 
                          as.Date('2025-04-10')))

```


## Merge
```{r armadata merge}

#merge our dependant and independant vars
armax_data = left_join(SPY_volatility, tweetcount, by="timestamp")
armax_data = left_join(armax_data, tweetdummy, by="timestamp")
armax_data = left_join(armax_data, tariff, by="timestamp")
armax_data = left_join(armax_data, trade, by="timestamp")
armax_data = left_join(armax_data, positive, by="timestamp")
armax_data = left_join(armax_data, negative, by="timestamp")

#convert NA to zeroes
armax_data$N[is.na(armax_data$N)] = 0
armax_data$dummy[is.na(armax_data$dummy)] = 0
armax_data$total_tariff[is.na(armax_data$total_tariff)] = 0
armax_data$total_trade[is.na(armax_data$total_trade)] = 0
armax_data$prop_positive[is.na(armax_data$prop_positive)] = 0
armax_data$prop_negative[is.na(armax_data$prop_negative)] = 0

```
\newpage

# ARMA-X Models

## Find Number of Lags
```{r JPR way to check for significance of lags, results='asis'}

lag_selector(y=armax_data$r_vol_h, xreg=armax_data$N,
             nb.lags=12, type="text")
lag_selector(y=armax_data$r_vol_h, xreg=armax_data$dummy,
             nb.lags=12, type="text")
lag_selector(y=armax_data$r_vol_h, xreg=armax_data$total_tariff,
             nb.lags=12, type="text")
lag_selector(y=armax_data$r_vol_h, xreg=armax_data$total_trade,
             nb.lags=12, type="text")

```





## Tweet Count on Volatility by hour
```{r ARMA-X count hourly volatility, results='asis'}

armax(armax_data$r_vol_h,xreg=armax_data$N,latex=F)

```


## Tweet Dummy on Volatility by hour
```{r ARMA-X dummy hourly, results='asis'}

armax(armax_data$r_vol_h,xreg=armax_data$dummy,latex=F)

```


## Tariff Mention on Volatility by hour
```{r ARMA-X tariff hourly, results='asis'}

armax(armax_data$r_vol_h,xreg=armax_data$total_tariff,latex=F)

```


## Trade Mention on Volatility by hour
```{r ARMA-X trade hourly, results='asis'}

armax(armax_data$r_vol_h,xreg=armax_data$total_trade,latex=F)

```








