---
title: "SPY SVAR Models"
output:
  pdf_document:
    toc: true
    fig_caption: true
    latex_engine: lualatex
header-includes: \usepackage{amsmath}
---
\newpage

# Setup

## Load packages & functions

```{r library_setup, results=FALSE, warning=FALSE, message=FALSE}
rm(list=ls())
require(tinytex) #LaTeX
require(ggplot2) #plots
require(AEC) #JP-Renne functions
require(AER) #NW formula
require(forecast) #time series stuff
require(expm) #matrix exponents
require(here) #directory finder
require(stringr) # analysis of strings, important for the detection in tweets
require(dplyr) #data management
require(lubridate) #data dates management
require(zoo) #for lagging
require(jtools) #tables
require(huxtable) #tables
require(lmtest) #reg tests
require(vroom) #for loading data
require(data.table) #for data filtering
require(sysid) #for ARMA-X modeling
require(sandwhich) #regression errors
require(stargazer) #nice reg tables
require(tidytext) #text mining
require(textstem) #lemmatization
require(quanteda) #tokenization
require(texreg) #arima tables
require(vars) #VAR models
require(xts) #time series objects
require(tseries) #includes adf test
require(quantmod)
require(TSA)
require(aTSA)
require(tibble)
require(FinTS)
require(kableExtra)
require(writexl)
require(purrr)

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
source(here("helperfunctions/truths_cleaning_function.R"))
source(here("helperfunctions/armax_functions.R"))
source(here("helperfunctions/var_irf.R"))

```


## Load Data


```{r datasetup, results=FALSE, warning=FALSE, message=FALSE}

#load final dataset
source(here("helperfunctions/full_data.R"))

#select timeframe 
Vdata = filter(data,between(timestamp, as.Date('2014-01-01'), as.Date('2025-05-07')))

```



# Some SVAR estimations

Note that this is not an exhaustive list of our VAR estimations, you can find 
more by going on /modeling/VAR/VAR_SPY_FULLMODELS.rmd or VAR_ASHR_FULLMODELS.rmd or VAR_VGK_FULLMODELS.rmd).


## Dummy variable 

Here we use a dummy variable which equal to one if Trump has made a post or 0 otherwise, taking into account the closed hour market posts.

```{r Estime dummy}
y = cbind(Vdata$dummy, Vdata$SPY_vol)
colnames(y)[1:2] <- c("dummy", "vol")
est.VAR <- VAR(y,p=6)

#extract results
mod_vol = est.VAR$varresult$vol
f = formula(mod_vol)
d = model.frame(mod_vol)
lm_clean = lm(f, data= d)

#apply Newey-West
nw_vcov = NeweyWest(lm_clean, lag=6)
nw_se = sqrt(diag(nw_vcov))

#t-stats
coef = coef(lm_clean)
t_stat = coef/nw_se

#recalculate p-values
robust = 2*(1-pt(abs(t_stat), df = df.residual(lm_clean)))

nw_se       <- nw_se[names(coef(lm_clean))]
robust      <- robust[names(coef(lm_clean))]

#table
screenreg(lm_clean, override.se = nw_se, override.pvalues = robust, digits = 6)


```





```{r effect of Vol on dummy}
#extract results
mod_post = est.VAR$varresult$dummy
ff = formula(mod_post)
dd = model.frame(mod_post)
lm_clean_post = lm(ff, data= dd)

#apply Newey-West
nw_vcov_post = NeweyWest(lm_clean_post, lag=6)
nw_se_post = sqrt(diag(nw_vcov_post))

#t-stats
coef_post = coef(lm_clean_post)
t_stat_post = coef_post/nw_se_post

#recalculate p-values
robust_post = 2*(1-pt(abs(t_stat_post), df = df.residual(lm_clean_post)))

nw_se_post       <- nw_se_post[names(coef(lm_clean_post))]
robust_post      <- robust_post[names(coef(lm_clean_post))]

#table
screenreg(lm_clean_post, override.se = nw_se_post, override.pvalues = robust_post, digits = 6)


```

```{r bp test}
#H0 test whether there is NOT heteroscedasticity. if less by alpha, then there is heteroscedasticity
bptest(lm_clean)



```

```{r B mat}

#Recreate a Robust Omega Matrix
U = residuals(est.VAR)
T = nrow(U)
L = 6 #number of lag
Omega = matrix(0, ncol(U), ncol(U))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l_ = t(U[(l+1):T, , drop=FALSE]) %*% U[1:(T-l), , drop=FALSE] /T
  if (l == 0){
    Omega = Omega + Gamma_l_
  } else {
    Omega = Omega + weight*(Gamma_l_ + t(Gamma_l_))
  }
}


#make the B matrix
loss <- function(param){
  #Define the restriction
  B <- matrix(c(param[1], param[2], 0, param[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X <- Omega - B %*% t(B)
  
  #loss function
  loss <- sum(X^2)
  return(loss)
}

res.opt <- optim(c(1, 0, 1), loss, method = "BFGS")
B.hat <- matrix(c(res.opt$par[1], res.opt$par[2], 0, res.opt$par[3]), ncol = 2)

print(cbind(Omega,B.hat %*% t(B.hat)))


```

```{r error of dum impact}
B.hat

```

```{r IRF 1dummy}
nb.sim = 7*7
#get back the coefficient of est.VAR
phi <- Acoef(est.VAR)
PHI = make.PHI(phi)

#take the constant
constant <- sapply(est.VAR$varresult, function(eq) coef(eq)["const"])
c=as.matrix(constant)

#Simulate the IRF
p <- length(phi)
n <- dim(phi[[1]])[1]


Y <- simul.VAR(c=c, Phi = phi, B = B.hat, nb.sim ,y0.star=rep(0, n*p),
                  indic.IRF = 1, u.shock = c(1,0))



Yd = data.frame(
  period = 1:nrow(Y),
  response = Y[,2])

ggplot(Yd,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of Dummy on Volatility")+
  ylab("")+
  xlab("") +
  theme_minimal()

```

```{r IRF 2Dummy}
ggplot(Yd,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of Dummy on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```





## Post Counts

```{r estimate with N}
y2 = cbind(Vdata$N, Vdata$SPY_vol)
colnames(y2)[1:2] <- c("N", "vol")
est.VAR2 <- VAR(y2,p=6)

#extract results
mod_vol2 = est.VAR2$varresult$vol
f2 = formula(mod_vol2)
d2 = model.frame(mod_vol2)
lm_clean2 = lm(f2, data= d2)

#apply Newey-West
nw_vcov2 = NeweyWest(lm_clean2, lag=6)
nw_se2 = sqrt(diag(nw_vcov2))

#t-stats
coef2 = coef(lm_clean2)
t_stat2 = coef2/nw_se2

#recalculate p-values
robust2 = 2*(1-pt(abs(t_stat2), df = df.residual(lm_clean2)))

nw_se2       <- nw_se2[names(coef(lm_clean2))]
robust2      <- robust2[names(coef(lm_clean2))]

#table
screenreg(lm_clean2, override.se = nw_se2, override.pvalues = robust2, digits = 6)
```

```{r effect of Vol on N}
#extract results
mod_post2 = est.VAR2$varresult$N
ff2 = formula(mod_post2)
dd2 = model.frame(mod_post2)
lm_clean_post2 = lm(ff2, data= dd2)

#apply Newey-West
nw_vcov_post2 = NeweyWest(lm_clean_post2, lag=6)
nw_se_post2 = sqrt(diag(nw_vcov_post2))

#t-stats
coef_post2 = coef(lm_clean_post2)
t_stat_post2 = coef_post2/nw_se_post2

#recalculate p-values
robust_post2 = 2*(1-pt(abs(t_stat_post2), df = df.residual(lm_clean_post2)))

nw_se_post2       <- nw_se_post2[names(coef(lm_clean_post2))]
robust_post2      <- robust_post2[names(coef(lm_clean_post2))]

#table
screenreg(lm_clean_post2, override.se = nw_se_post2, override.pvalues = robust_post2, digits = 6)


```

```{r B mat2}
#Recreate a Robust Omega Matrix
U2 = residuals(est.VAR2)
T2 = nrow(U2)
Omega2 = matrix(0, ncol(U2), ncol(U2))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l_2 = t(U2[(l+1):T2, , drop=FALSE]) %*% U2[1:(T2-l), , drop=FALSE] /T2
  if (l == 0){
    Omega2 = Omega2 + Gamma_l_2
  } else {
    Omega2 = Omega2 + weight*(Gamma_l_2 + t(Gamma_l_2))
  }
}

#make the B matrix
loss2 <- function(param2){
  #Define the restriction
  B2 <- matrix(c(param2[1], param2[2], 0, param2[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X2 <- Omega2 - B2 %*% t(B2)
  
  #loss function
  loss2 <- sum(X2^2)
  return(loss2)
}

res.opt2 <- optim(c(1, 0, 1), loss2, method = "BFGS")
B.hat2 <- matrix(c(res.opt2$par[1], res.opt2$par[2], 0, res.opt2$par[3]), ncol = 2)

print(cbind(Omega2,B.hat2 %*% t(B.hat2)))


```

```{r shock by N}
B.hat2

```

```{r IRF 1N}
#get back the coefficient of est.VAR
phi2 <- Acoef(est.VAR2)
PHI2 = make.PHI(phi2)

#take the constant
constant2 <- sapply(est.VAR2$varresult, function(eq) coef(eq)["const"])
c2=as.matrix(constant2)

#Simulate the IRF
p2 <- length(phi2)
n2 <- dim(phi2[[1]])[1]

Y2 <- simul.VAR(c=c2, Phi = phi2, B = B.hat2, nb.sim ,y0.star=rep(0, n2*p2),
                  indic.IRF = 1, u.shock = c(1,0))


#Plot the IRF
Yd2 = data.frame(
  period = 1:nrow(Y2),
  response = Y2[,2])

ggplot(Yd2,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of N on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r IRF N5}
ggplot(Yd2,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of N on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r does N granger cause vol}
grangertest(y2[,c("N", "vol")], order = 6)

```

```{r does vol granger cause N}
grangertest(y2[,c("vol", "N")], order = 6)

```




## Trade Mention

```{r estimate trade}
y4 = cbind(Vdata$trade, Vdata$SPY_vol)
colnames(y4)[1:2] <- c("trade", "vol")
est.VAR4 <- VAR(y4,p=6)

#extract results
mod_vol4 = est.VAR4$varresult$vol
f4 = formula(mod_vol4)
d4 = model.frame(mod_vol4)
lm_clean4 = lm(f4, data= d4)

#apply Newey-West
nw_vcov4 = NeweyWest(lm_clean4, lag=6)
nw_se4 = sqrt(diag(nw_vcov4))

#t-stats
coef4 = coef(lm_clean4)
t_stat4 = coef4/nw_se4

#recalculate p-values
robust4 = 2*(1-pt(abs(t_stat4), df = df.residual(lm_clean4)))

nw_se4       <- nw_se4[names(coef(lm_clean4))]
robust4      <- robust4[names(coef(lm_clean4))]

#table
screenreg(lm_clean4, override.se = nw_se4, override.pvalues = robust4, digits = 6)
```

```{r effect of Vol on trade}
#Table for the effect of volatility on posts for variable trade
#extract results
mod_post4 = est.VAR4$varresult$trade
ff4 = formula(mod_post4)
dd4 = model.frame(mod_post4)
lm_clean_post4 = lm(ff4, data= dd4)

#apply Newey-West
nw_vcov_post4 = NeweyWest(lm_clean_post4, lag=6)
nw_se_post4 = sqrt(diag(nw_vcov_post4))

#t-stats
coef_post4 = coef(lm_clean_post4)
t_stat_post4 = coef_post4/nw_se_post4

#recalculate p-values
robust_post4 = 2*(1-pt(abs(t_stat_post4), df = df.residual(lm_clean_post4)))

nw_se_post4       <- nw_se_post4[names(coef(lm_clean_post4))]
robust_post4      <- robust_post4[names(coef(lm_clean_post4))]

#table
screenreg(lm_clean_post4, override.se = nw_se_post4, override.pvalues = robust_post4, digits = 6)


```

```{r B mat4}
#Recreate a Robust Omega Matrix
U4 = residuals(est.VAR4)
T4 = nrow(U4)
Omega4 = matrix(0, ncol(U4), ncol(U4))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l_4 = t(U4[(l+1):T4, , drop=FALSE]) %*% U4[1:(T4-l), , drop=FALSE] /T4
  if (l == 0){
    Omega4 = Omega4 + Gamma_l_4
  } else {
    Omega4 = Omega4 + weight*(Gamma_l_4 + t(Gamma_l_4))
  }
}


#make the B matrix
loss4 <- function(param4){
  #Define the restriction
  B4 <- matrix(c(param4[1], param4[2], 0, param4[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X4 <- Omega4 - B4 %*% t(B4)
  
  #loss function
  loss4 <- sum(X4^2)
  return(loss4)
}

res.opt4 <- optim(c(1, 0, 1), loss4, method = "BFGS")
B.hat4 <- matrix(c(res.opt4$par[1], res.opt4$par[2], 0, res.opt4$par[3]), ncol = 2)

print(cbind(Omega4,B.hat4 %*% t(B.hat4)))



```

```{r shock by trade}
B.hat4

```

```{r IRF tradeeee}
#get back the coefficient of est.VAR
phi4 <- Acoef(est.VAR4)
PHI4 = make.PHI(phi4)

#take the constant
constant4 <- sapply(est.VAR4$varresult, function(eq) coef(eq)["const"])
c4=as.matrix(constant4)

#Simulate the IRF
p4 <- length(phi4)
n4 <- dim(phi4[[1]])[1]

Y4 <- simul.VAR(c=c4, Phi = phi4, B = B.hat4, nb.sim ,y0.star=rep(0, n4*p4),
                  indic.IRF = 1, u.shock = c(1,0))


#Plot the IRF
Yd4 = data.frame(
  period = 1:nrow(Y4),
  response = Y4[,2])

ggplot(Yd4,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of Trade on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r IRF trade}
ggplot(Yd4,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of trade on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r does vol granger cause trade}

grangertest(y4[,c("vol","trade")], order = 6)



```

```{r does trade granger cause vol}

grangertest(y4[,c("trade", "vol")], order = 6)


```




# China Mention

```{r estime China}

ychina = cbind(Vdata$china, Vdata$SPY_vol)
colnames(ychina)[1:2] <- c("china", "vol")
est.VARchina <- VAR(ychina,p=6)

#extract results
mod_volchina = est.VARchina$varresult$vol
fchina = formula(mod_volchina)
dchina = model.frame(mod_volchina)
lm_cleanchina = lm(fchina, data= dchina)

#apply Newey-West
nw_vcovchina = NeweyWest(lm_cleanchina, lag=6)
nw_sechina = sqrt(diag(nw_vcovchina))

#t-stats
coefchina = coef(lm_cleanchina)
t_statchina = coefchina/nw_sechina

#recalculate p-values
robustchina = 2*(1-pt(abs(t_statchina), df = df.residual(lm_cleanchina)))

nw_sechina       <- nw_sechina[names(coef(lm_cleanchina))]
robustchina      <- robustchina[names(coef(lm_cleanchina))]

#table
screenreg(lm_cleanchina, override.se = nw_sechina, override.pvalues = robustchina, digits = 6)
```

```{r effect of Vol on china}
#Table for the effect of volatility on posts for variable china
#extract results
mod_postchina = est.VARchina$varresult$china
ffchina = formula(mod_postchina)
ddchina = model.frame(mod_postchina)
lm_clean_postchina = lm(ffchina, data= ddchina)

#apply Newey-West
nw_vcov_postchina = NeweyWest(lm_clean_postchina, lag=6)
nw_se_postchina = sqrt(diag(nw_vcov_postchina))

#t-stats
coef_postchina = coef(lm_clean_postchina)
t_stat_postchina = coef_postchina/nw_se_postchina

#recalculate p-values
robust_postchina = 2*(1-pt(abs(t_stat_postchina), df = df.residual(lm_clean_postchina)))

nw_se_postchina       <- nw_se_postchina[names(coef(lm_clean_postchina))]
robust_postchina      <- robust_postchina[names(coef(lm_clean_postchina))]

#table
screenreg(lm_clean_postchina, override.se = nw_se_postchina, override.pvalues = robust_postchina, digits = 6)


```

```{r B mat china}
#Recreate a Robust Omega Matrix
Uchina = residuals(est.VARchina)
Tchina = nrow(Uchina)
Omegachina = matrix(0, ncol(Uchina), ncol(Uchina))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l_china = t(Uchina[(l+1):Tchina, , drop=FALSE]) %*% Uchina[1:(Tchina-l), , drop=FALSE] /Tchina
  if (l == 0){
    Omegachina = Omegachina + Gamma_l_china
  } else {
    Omegachina = Omegachina + weight*(Gamma_l_china + t(Gamma_l_china))
  }
}


#make the B matrix
losschina <- function(paramchina){
  #Define the restriction
  Bchina <- matrix(c(paramchina[1], paramchina[2], 0, paramchina[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  Xchina <- Omegachina - Bchina %*% t(Bchina)
  
  #loss function
  losschina <- sum(Xchina^2)
  return(losschina)
}

res.optchina <- optim(c(1, 0, 1), losschina, method = "BFGS")
B.hatchina <- matrix(c(res.optchina$par[1], res.optchina$par[2], 0, res.optchina$par[3]), ncol = 2)

print(cbind(Omegachina,B.hatchina %*% t(B.hatchina)))



```

```{r shock by china}
B.hatchina


```

```{r IRF china1}
#get back the coefficient of est.VAR
phichina <- Acoef(est.VARchina)
PHIchina = make.PHI(phichina)

#take the constant
constantchina <- sapply(est.VARchina$varresult, function(eq) coef(eq)["const"])
cchina=as.matrix(constantchina)

#Simulate the IRF
pchina <- length(phichina)
nchina <- dim(phichina[[1]])[1]

Ychina <- simul.VAR(c=cchina, Phi = phichina, B = B.hatchina, nb.sim ,y0.star=rep(0, nchina*pchina),
                  indic.IRF = 1, u.shock = c(1,0))


#Plot the IRF
Ydchina = data.frame(
  period = 1:nrow(Ychina),
  response = Ychina[,2])

ggplot(Ydchina,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of China on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r IRF China}
ggplot(Ydchina,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of China on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r does vol granger cause china}

grangertest(ychina[,c("vol", "china")], order = 6)


```

```{r does china granger cause vol}

grangertest(ychina[,c("china", "vol")], order = 6)


```





# Split Terms

Here we look for the first and second mandate effect of posts. 
We will use the tariff variable as a proxy for the posts.



```{r datasetup2, results=FALSE, warning=FALSE, message=FALSE}

# First and Second Mandate

#first term
Vdata_f = filter(data,between(timestamp, as.Date('2017-01-20'), as.Date('2021-01-20')))

#second term
Vdata_s = filter(data,between(timestamp, as.Date('2025-01-20'), as.Date('2025-05-07')))

```


## First mandate

```{r first mandate dum, warning=FALSE, message=FALSE, results="asis"}
y_f_d = cbind(Vdata_f$dummy, Vdata_f$SPY_vol)
colnames(y_f_d)[1:2] <- c("dummy", "vol")
est.VAR_f_d <- VAR(y_f_d,p=6)

#extract results
mod_vol_f_d = est.VAR_f_d$varresult$vol
f_f_d = formula(mod_vol_f_d)
d_f_d = model.frame(mod_vol_f_d)
lm_clean_f_d = lm(f_f_d, data= d_f_d)

#apply Newey-West
nw_vcov_f_d = NeweyWest(lm_clean_f_d, lag=6)
nw_se_f_d = sqrt(diag(nw_vcov_f_d))

#t-stats
coef_f_d = coef(lm_clean_f_d)
t_stat_f_d = coef_f_d/nw_se_f_d

#recalculate p-values
robust_f_d = 2*(1-pt(abs(t_stat_f_d), df = df.residual(lm_clean_f_d)))

nw_se_f_d       <- nw_se_f_d[names(coef(lm_clean_f_d))]
robust_f_d      <- robust_f_d[names(coef(lm_clean_f_d))]

#table
screenreg(lm_clean_f_d, override.se = nw_se_f_d, override.pvalues = robust_f_d, digits = 6)
```

```{r effect of Vol on dummy first}
#Table for the effect of volatility on posts for variable dummy
#extract results
mod_post_f_d = est.VAR_f_d$varresult$dummy
ff_f_d = formula(mod_post_f_d)
dd_f_d = model.frame(mod_post_f_d)
lm_clean_post_f_d = lm(ff_f_d, data= dd_f_d)

#apply Newey-West
nw_vcov_post_f_d = NeweyWest(lm_clean_post_f_d, lag=6)
nw_se_post_f_d = sqrt(diag(nw_vcov_post_f_d))

#t-stats
coef_post_f_d = coef(lm_clean_post_f_d)
t_stat_post_f_d = coef_post_f_d/nw_se_post_f_d

#recalculate p-values
robust_post_f_d = 2*(1-pt(abs(t_stat_post_f_d), df = df.residual(lm_clean_post_f_d)))

nw_se_post_f_d       <- nw_se_post_f_d[names(coef(lm_clean_post_f_d))]
robust_post_f_d      <- robust_post_f_d[names(coef(lm_clean_post_f_d))]


#table
screenreg(lm_clean_post_f_d, override.se = nw_se_post_f_d, override.pvalues = robust_post_f_d, digits = 6)


```

```{r B mat first mandate dum, warning=FALSE, message=FALSE}
#Construct the Robust Omega Matrix
U_f_d = residuals(est.VAR_f_d)
T_f_d = nrow(U_f_d)
Omega_f_d = matrix(0, ncol(U_f_d), ncol(U_f_d))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l__f_d = t(U_f_d[(l+1):T_f_d, , drop=FALSE]) %*% U_f_d[1:(T_f_d-l), , drop=FALSE] /T_f_d
  if (l == 0){
    Omega_f_d = Omega_f_d + Gamma_l__f_d
  } else {
    Omega_f_d = Omega_f_d + weight*(Gamma_l__f_d + t(Gamma_l__f_d))
  }
}


#make the B matrix
loss_f_d <- function(param_f_d){
  #Define the restriction
  B_f_d <- matrix(c(param_f_d[1], param_f_d[2], 0, param_f_d[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X_f_d <- Omega_f_d - B_f_d %*% t(B_f_d)
  
  #loss function
  loss_f_d <- sum(X_f_d^2)
  return(loss_f_d)
}

res.opt_f_d <- optim(c(1, 0, 1), loss_f_d, method = "BFGS")
B.hat_f_d <- matrix(c(res.opt_f_d$par[1], res.opt_f_d$par[2], 0, res.opt_f_d$par[3]), ncol = 2)

print(cbind(Omega_f_d,B.hat_f_d %*% t(B.hat_f_d)))

```

```{r shock by _f_d}
B.hat_f_d

```

```{r IRF first dum, warning=FALSE, message=FALSE}
#get back the coefficient of est.VAR
phi_f_d <- Acoef(est.VAR_f_d)
PHI_f_d = make.PHI(phi_f_d)

#take the constant
constant_f_d <- sapply(est.VAR_f_d$varresult, function(eq) coef(eq)["const"])
c_f_d=as.matrix(constant_f_d)

#Simulate the IRF
p_f_d <- length(phi_f_d)
n_f_d <- dim(phi_f_d[[1]])[1]

Y_f_d <- simul.VAR(c=c_f_d, Phi = phi_f_d, B = B.hat_f_d, nb.sim ,y0.star=rep(0, n_f_d*p_f_d),
                  indic.IRF = 1, u.shock = c(1,0))


#Plot the IRF
Yd_f_d = data.frame(
  period = 1:nrow(Y_f_d),
  response = Y_f_d[,2])

ggplot(Yd_f_d,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of First Term Dummy on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r IRF First Mandate Dummy}
ggplot(Yd_f_d,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of First Mandate Dummy on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r granger_f_d, warning=FALSE, message=FALSE}

#does vol granger cause dummy
grangertest(y_f_d[,c("vol","dummy")], order =6)

#does dummy granger cause vol
grangertest(y_f_d[,c("dummy", "vol")], order =6)

```



## Second Mandate

```{r second mandate dum, warning=FALSE, message=FALSE, results="asis"}

y_s_d = cbind(Vdata_s$dummy, Vdata_s$SPY_vol)
colnames(y_s_d)[1:2] <- c("dummy", "vol")
est.VAR_s_d <- VAR(y_s_d,p=6)

#extract results
mod_vol_s_d = est.VAR_s_d$varresult$vol
f_s_d = formula(mod_vol_s_d)
d_s_d = model.frame(mod_vol_s_d)
lm_clean_s_d = lm(f_s_d, data= d_s_d)

#apply Newey-West
nw_vcov_s_d = NeweyWest(lm_clean_s_d, lag=6)
nw_se_s_d = sqrt(diag(nw_vcov_s_d))

#t-stats
coef_s_d = coef(lm_clean_s_d)
t_stat_s_d = coef_s_d/nw_se_s_d

#recalculate p-values
robust_s_d = 2*(1-pt(abs(t_stat_s_d), df = df.residual(lm_clean_s_d)))

nw_se_s_d       <- nw_se_s_d[names(coef(lm_clean_s_d))]
robust_s_d      <- robust_s_d[names(coef(lm_clean_s_d))]

#table
screenreg(lm_clean_s_d, override.se = nw_se_s_d, override.pvalues = robust_s_d, digits = 6)
```

```{r effect of Vol on dummy second}
#Table for the effect of volatility on posts for variable dummy
#extract results
mod_post_s_d = est.VAR_s_d$varresult$dummy
ff_s_d = formula(mod_post_s_d)
dd_s_d = model.frame(mod_post_s_d)
lm_clean_post_s_d = lm(ff_s_d, data= dd_s_d)

#apply Newey-West
nw_vcov_post_s_d = NeweyWest(lm_clean_post_s_d, lag=6)
nw_se_post_s_d = sqrt(diag(nw_vcov_post_s_d))

#t-stats
coef_post_s_d = coef(lm_clean_post_s_d)
t_stat_post_s_d = coef_post_s_d/nw_se_post_s_d

#recalculate p-values
robust_post_s_d = 2*(1-pt(abs(t_stat_post_s_d), df = df.residual(lm_clean_post_s_d)))

nw_se_post_s_d       <- nw_se_post_s_d[names(coef(lm_clean_post_s_d))]
robust_post_s_d      <- robust_post_s_d[names(coef(lm_clean_post_s_d))]

#table
screenreg(lm_clean_post_s_d, override.se = nw_se_post_s_d, override.pvalues = robust_post_s_d, digits = 6)


```

```{r B mat second mandate dum, warning=FALSE, message=FALSE}
#Construct the Robust Omega Matrix
U_s_d = residuals(est.VAR_s_d)
T_s_d = nrow(U_s_d)
Omega_s_d = matrix(0, ncol(U_s_d), ncol(U_s_d))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l__s_d = t(U_s_d[(l+1):T_s_d, , drop=FALSE]) %*% U_s_d[1:(T_s_d-l), , drop=FALSE] /T_s_d
  if (l == 0){
    Omega_s_d = Omega_s_d + Gamma_l__s_d
  } else {
    Omega_s_d = Omega_s_d + weight*(Gamma_l__s_d + t(Gamma_l__s_d))
  }
}


#make the B matrix
loss_s_d <- function(param_s_d){
  #Define the restriction
  B_s_d <- matrix(c(param_s_d[1], param_s_d[2], 0, param_s_d[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X_s_d <- Omega_s_d - B_s_d %*% t(B_s_d)
  
  #loss function
  loss_s_d <- sum(X_s_d^2)
  return(loss_s_d)
}

res.opt_s_d <- optim(c(1, 0, 1), loss_s_d, method = "BFGS")
B.hat_s_d <- matrix(c(res.opt_s_d$par[1], res.opt_s_d$par[2], 0, res.opt_s_d$par[3]), ncol = 2)

print(cbind(Omega_s_d,B.hat_s_d %*% t(B.hat_s_d)))

```

```{r shock by _s_d}
B.hat_s_d


```

```{r IRF second dum, warning=FALSE, message=FALSE}
#get back the coefficient of est.VAR
phi_s_d <- Acoef(est.VAR_s_d)
PHI_s_d = make.PHI(phi_s_d)

#take the constant
constant_s_d <- sapply(est.VAR_s_d$varresult, function(eq) coef(eq)["const"])
c_s_d=as.matrix(constant_s_d)

#Simulate the IRF
p_s_d <- length(phi_s_d)
n_s_d <- dim(phi_s_d[[1]])[1]

Y_s_d <- simul.VAR(c=c_s_d, Phi = phi_s_d, B = B.hat_s_d, nb.sim ,y0.star=rep(0, n_s_d*p_s_d),
                  indic.IRF = 1, u.shock = c(1,0))


#Plot the IRF
Yd_s_d = data.frame(
  period = 1:nrow(Y_s_d),
  response = Y_s_d[,2])

ggplot(Yd_s_d,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of Second Term Dummy on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r IRF Second Mandate Dummy}
ggplot(Yd_s_d,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of Second Mandate Dummy on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r granger_s_d, warning=FALSE, message=FALSE}

#does vol granger cause dummy
grangertest(y_s_d[,c("vol","dummy")], order =6)

#does dummy granger cause vol
grangertest(y_s_d[,c("dummy", "vol")], order =6)

```

