---
title: "Testing"
output:
  pdf_document: 
    toc: true
    fig_caption: yes
header-includes:
  - \usepackage{amsmath}
---
\newpage

```{r library_setup, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
rm(list=ls())
require(tinytex) #LaTeX
require(ggplot2) #plots
require(AEC) #JP-Renne functions
require(forecast) #time series stuff
require(expm) #matrix exponents
require(here) #directory finder
require(stringr) # analysis of strings, important for the detection in tweets
require(dplyr) #data management
require(lubridate) #data dates management
require(zoo) #for lagging
require(jtools) #tables
require(huxtable) #tables
require(lmtest) #reg tests
require(vroom) #for loading data
require(data.table) #for data filtering
require(RColorBrewer)
require(wordcloud)
require(tidyr)
require(randomForest)
require(tidytext)
require(textstem)
require(tidyverse)
require(tm)
require(SnowballC)
require(quanteda.textplots)
require(quantmod)
require(quanteda)
require(rvest)
require(httr)
require(xml2)
require(textdata)
require(sentimentr)
require(syuzhet)
require(text)

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
source(here("helperfunctions/truths_cleaning_function.R"))
```


# Data 

## Raw Political Data
```{r political rawdata_setup, results=FALSE, warning=FALSE, message=FALSE}

#political shocks
raw_truths <- read.csv(here("data/political_data", "truths_new.csv"))
#raw_tweets <- read.csv(here("data/political_data", "tweets.csv"))

```

## Raw Data
```{r financial rawdata_setup, results=FALSE, warning=FALSE, message=FALSE}
#market prices (loads and names them automatically)
#raw_ONEQ <- read.csv(here("data/market_data", "ONEQ.csv")) #USA
#raw_SMI <- read.csv(here("data/market_data", "SMI.csv")) #CH
#raw_VTHR <- read.csv(here("data/market_data", "VTHR.csv")) #USA
#raw_VTI <- read.csv(here("data/market_data", "VTI.csv")) #USA
#raw_DAX <- read.csv(here("data/market_data", "DAX.csv")) #DE
#raw_ASHR <- read.csv(here("data/market_data", "ASHR.csv")) #CHINA
raw_SPYy <- read.csv(here("data/market_data", "Spyqyahoo.csv")) #yahoo

#S&P500
data_loader(symbol="SPY")

#STOXX50
data_loader(symbol="VGK")




#CSI 300 (China)
data_loader(symbol="ASHR")

```


## Daily Data
```{r dailydata, results=FALSE, warning=FALSE, message=FALSE}

#political shocks


#market prices
day_SPY_0409 = filter(raw_SPY, str_detect(timestamp, "^2025-04-09")) #9th of april
day_SPY_0409$timestamp = as.POSIXct(day_SPY_0409$timestamp, 
                                    format = "%Y-%m-%d %H:%M:%S", tz = "EST")

yahoo_ds0409 = filter(raw_SPYy, str_detect(Date, "^2025-04-09"))
yahoo_ds0409$Date = as.POSIXct(yahoo_ds0409$Date, 
                                    format = "%Y-%m-%dT%H:%M:%S", tz = "UTC")
yahoo_ds0409$Date = with_tz(yahoo_ds0409$Date, "EST")


#extract a particular month
SPY_24_09 = month_selector(raw_SPY,2024,09) #november 2024


#extract a particular year
SPY_24 = year_selector(raw_SPY,2024) #2024

```


# Plots

## Total 
```{r total market plots}

#SPY
ggplot(raw_SPY, aes(x = as.POSIXct(timestamp), y = close)) +
  geom_point(color = "blue", size = 0.01) +
  geom_line(aes(group=1), color="blue", linewidth=0.05) +
  labs(title = "SPY Price Over Time",
       x = "Time",
       y = "Close Price") +
  scale_x_datetime(date_labels = "%b %Y", date_breaks = "6 month") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
```


## Per Day
```{r daily market plots}

#SPY Source: alpha
ggplot(day_SPY_0409, aes(x = timestamp, y = close)) +
  geom_point(color = "blue", size = 0.01) +
  geom_line(aes(group=1)) +
  labs(title = "SPY alpha Price April 9th",
       x = "Time",
       y = "Close Price") +
   scale_x_datetime(date_labels = "%H:%M",  
                    date_breaks = "60 min") +
   theme_minimal() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))


#SPY Source: yahoo
ggplot(yahoo_ds0409, aes(x = Date, y = Close)) +
  geom_point(color = "blue", size = 0.01) +
  geom_line(aes(group=1)) +
  labs(title = "SPY yahoo Price April 9th",
       x = "Time",
       y = "Close Price") +
   scale_x_datetime(date_labels = "%H:%M",  
                    date_breaks = "60 min") +
   theme_minimal() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))



```

# Time Series Analysis
```{r time series}

acf(log(day_SPY_0409$close))
pacf(log(day_SPY_0409$close))

acf(log(raw_SPY$close))
pacf(log(raw_SPY$close))

AR1 = arima(day_SPY_0409$close,c(1,0,0),method="ML")
AR2 = arima(day_SPY_0409$close,c(2,0,0),method="ML")
AR3 = arima(day_SPY_0409$close,c(3,0,0),method="ML")
table1 = export_summs(AR1,AR2,AR3, model.names = c("AR1","AR2","AR3"), digits = 4)
huxtable::caption(table1) <- "AR Estimations"
huxtable::set_width(table1, 0.8)

AR1res = as.numeric(AR1$residuals)
AR1res_lagged <- lag(AR1res, 1)
iidcheck1 = lm(AR1res ~ AR1res_lagged)
AR2res = as.numeric(AR2$residuals)
AR2res_lagged <- lag(AR2res, 1)
iidcheck2 = lm(AR2res ~ AR2res_lagged)
AR3res = as.numeric(AR3$residuals)
AR3res_lagged <- lag(AR3res, 1)
iidcheck3 = lm(AR3res ~ AR3res_lagged)
table2 = export_summs(iidcheck1,iidcheck2,iidcheck3, 
             model.names = c("AR1 Residuals","AR2 Residuals","AR3 Residuals"), 
             digits = 4)
huxtable::caption(table2) <- "Checking Residuals"
huxtable::set_width(table2, 0.8)
```

# Volatility 


## JPR Formula
$$
\begin{aligned}
  v_t &= \frac{1}{N}\sum_{i=1}^N(\Delta p_{t,i})^2 \\
  &\text{where } \Delta p_t \text{ is the difference in price (open - close)} \\
  &\text{and i represents every minute}
\end{aligned}
$$

```{r JPR}
#extract a particular day
SPY_25_04_02 = day_selector(raw_SPY,2025,04,02) #april 2nd 2025

#let's plot it
price_plotter_day(SPY_25_04_02,"SPY Price on April 2nd 2025") 

#quick
quickplot = function(x){price_plotter_day(day_selector(raw_SPY,2025,04,x),"SPY Price 2025")}
quickplot(9)

#realized volatility 
delta_price = SPY_25_04_02$close - SPY_25_04_02$open
delta_price_sqr = delta_price^2
SPY_25_04_02 = cbind(day_selector(raw_SPY,2025,04,02),delta_price_sqr)
v_t = sum(delta_price_sqr) / length(delta_price)

#or is it like this??
#realized volatility method2
p_t = SPY_25_04_02$close
p_t_1 <- lag(p_t, 1)
delta_price2 = p_t_1 - p_t
v_t2 = sum((na.omit(delta_price2))^2) / length(na.omit(delta_price2))

```

```{r JPR volatility compute}
#average per day (outputs scalar)
r.vol_day(SPY_25_04_02) 

#average per day for each day in a month (outputs vector of each day's realised volatility)
r.vol_month(SPY_24_09) 

#for each hour in a day (outputs a vector of each hour's realised volatility)
r.vol_day_hour(SPY_25_04_02) 

#for each hour in a day for each day in a month (outputs a matrix)
month_hour = r.vol_month_hour(SPY_24_09)
huxtable(head(data.frame(month_hour)))


#avg per day for each month of any dataset
#works for datasets with more than 1 year!
vol_SPY_daily = r.vol_daily(raw_SPY,merge=F)
head(vol_SPY_daily)

#can then filter out years, months, or days
vol_24d = year_selector(vol_SPY_daily,2024)
vol_24_08d = month_selector(vol_SPY_daily,2024,08)
vol_24_11_04d = day_selector(vol_SPY_daily,2024,11,04) #scalar


#avg per hour for each day of each month of any dataset
#works for datasets with more than 1 year!
vol_SPY_hourly = r.vol_hourly(raw_SPY,merge=F)
head(vol_SPY_hourly)

#can then filter out years, months, or days
vol_24h = year_selector(vol_SPY_hourly,2024)
vol_24_08h = month_selector(vol_SPY_hourly,2024,08)
vol_24_11_04h = day_selector(vol_SPY_hourly,2024,11,04) #vector

```


```{r SPY volatility plots}

#avg per day volatility all time
dvol_plotter(vol_SPY_daily,breaks="yearly",
             title="SPY Volatility Since 2019")

#avg per day volatility in a year
dvol_plotter(vol_24d,breaks="monthly",
             title="Realised Volatility - SPY 2024")

#avg per day volatility in a month
dvol_plotter(vol_24_08d,breaks="daily",
             title="Realised Volatility - SPY August 2024")


#hourly volatility all time
hvol_plotter(vol_SPY_hourly,breaks="yearly",
             title="SPY Volatility Since 2019")

#hourly volatility in a year
hvol_plotter(vol_24h,breaks="monthly",
             title="Realised Volatility - SPY 2024")

#hourly volatility in a month
hvol_plotter(vol_24_08h,breaks="daily",
             title="Realised Volatility - SPY August 2024")

#hourly volatility in a day
hvol_plotter(vol_24_11_04h,breaks="hourly",
             title="Realised Volatility - SPY 4th of November 2024")

```


## Garman and Klass (1980) Formula
Note that this formula uses open-high-low-close information. \\
This model is based on the assumption that price returns follow a Wiener process with zero drift and constant infinitesimal variance. It’s constructed by minimizing the variance of a quadratic estimator subject to the constraints of price and time symmetry and scale invariance of volatility. Source: https://assets.bbhub.io/professional/sites/10/intraday_volatility-3.pdf
$$
\begin{aligned}
  V_{ohlc} = 0.5[log(H)-log(L)]^2 - [2log(2)-1][log(C)-log(O)]^2
\end{aligned}
$$
```{r GnK}
#extract a particular day
day_SPY_0402 = day_selector(raw_SPY,2025,04,02) #april 2nd 2025

#variables
C = day_SPY_0402$close 
O = day_SPY_0402$open
H = day_SPY_0402$high 
L = day_SPY_0402$low

#realized volatility 
V_ohlc = 0.5*(log(H)-log(L))^2 - (2*log(2)-1)*(log(C)-log(O))^2
v_ohlc = sqrt(V_ohlc)
day_SPY_0402 = cbind(day_selector(raw_SPY,2025,04,02),V_ohlc)
avg = sum(V_ohlc) / length(V_ohlc)



```



# Tweets

```{r playing around}

#cleanup
truthsbackup <- truths_processer(raw_truths) 
truths = as.data.table(truthsbackup)
names(truths)[names(truths) == 'date_time_parsed'] <- 'timestamp'
truths <- truths[order(truths$timestamp, decreasing=T), ]

#count by hour
truth_count = truths[, .N, by=.(year(timestamp), month(timestamp), day(timestamp), hour(timestamp))] 

#fix timestamp
truth_count$timestamp = as.POSIXct(sprintf("%04d-%02d-%02d %02d:00:00", truth_count$year, 
                             truth_count$month, truth_count$day, 
                             truth_count$hour), format = "%Y-%m-%d %H:00:00")

#remove useless columns
truth_count = select(truth_count, timestamp, N)


```



























