---
bibliography: macroeconometrics_citations.bib  #
csl: apa.csl
link-citations: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r, warning=FALSE, echo=FALSE, cache=FALSE}
require("here")
require("stringr")
require("dplyr")
require("ggplot2")
require("lubridate")

truths_raw <- read.csv(here("data/mothership", "social.csv"))

truths <- truths_raw %>%
  mutate(
    # Use POSIX 'timestamp' directly
    date_time_parsed = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S"),
    
    # Extract date only for plot
    day = as.Date(date_time_parsed),
    
    # Extract time only for plot
    time = format(date_time_parsed, "%H:%M"),
    
    # Convert time to numeric hours & minutes as fractions
    time_numeric = hour(date_time_parsed) + minute(date_time_parsed) / 60,
    
    # Shift time such that y = 0 corresponds to 12 PM
    time_shifted = time_numeric - 12
  )

```

# Introduction

## Motivation

Over the past 15 years, social media has become an important
communication tool for politicians. One of the pioneers of this novel
approach has been Donald Trump, the 45th and 47th President of the United
States. His prominent level of posting is clearly visible on Figure \@ref(fig:fig1),
where the gap between 2021 and 2022 represents his ban from Twitter after the 
January 6th riots.[^1]

[^1]: Includes both Posts and Reposts

The content of his posts can sometimes have announcements or teases of future
political decisions. Note the recent infamous "THIS IS A GREAT TIME TO BUY!!! DJT"
post sent just an hour before lifting his reciprocal tariffs. It is then not 
improbable that agents in financial markets might take this information into 
account in their decision making. This question has been asked before in the 
literature, primarily focusing on his first term. 

This brings us to our research question:  Do Donald Trump's posts impact market volatility?

    
```{r fig1, fig.width=10, fig.height=5, echo=FALSE, fig.cap="Terminally Online: Trump's Twitter & Truth Social Posts (EDT)", warning=FALSE, cache=FALSE}
 #Create the scatter plot
ggplot(truths, aes(x = day, y = time_shifted)) +
  geom_point(alpha = 0.5, color = "darkblue", size = 0.55) +  # Transparancy to create "heatmap"
  scale_y_continuous(
    breaks = seq(-12, 12, by = 3),  # Custom Y scale
    labels = c("00:00", "03:00", "06:00", "09:00", "12:00", "15:00", "18:00", "21:00", "24:00")  # 24-hour format labels
  ) +
  labs(title = "Terminally Online: Trumps Twitter & Truth Social Posts (EDT)",
       x = "",
       y = "") +
  theme_classic() +
  
  
  # X Axis adjustments
  scale_x_date(
    date_labels = "%b %Y",  # Format labels to show month and year
    date_breaks = "9 months"
  ) +
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  
  # Add market opening/closing lines
  geom_hline(yintercept = (9 + 30 / 60) - 12, linetype = "longdash", color = "red") + 
  geom_hline(yintercept = 16 - 12, linetype = "dashed", color = "red") +
  
  # theme adjustments
  theme(
    panel.grid.minor = element_blank(),  
    panel.grid.major = element_line(linewidth = 0.5),  # Major gridlines only
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )+
  
  # Add caption  
  labs(caption = "Every blue dot represents a post or repost. Red lines indicate market opening hours.") +
  theme(plot.caption = element_text(hjust = 0, face = "italic", size = 10))
  
```



## Literature Review


Information is one of the most valuable assets in the financial market.
Its importance lies at the core of the "Efficient Market Hypothesis", 
which states that the prices of assets fully reflect all
available information, adjusting immediately to any new data
(@famaAdjustmentStockPrices2003), and thereby creating a strong demand
for information flow. In addition, the “Mixture of Distribution
Hypothesis” states that the release of new information is closely linked
to movements in both realized and implied volatility
(@andersenReturnVolatilityTrading1996, @frenchStockReturnVariances1986,
@vlastakisInformationDemandStock2012).

Consequently, a large part of the literature has focused on the relationship
between announcements, news and market activity. For example,
@schumakerTextualAnalysisStock2009 use various linguistic and textual
representations derived from financial news to predict stock market
prices. Similarly, @ederingtonHowMarketsProcess1993 analyze the impact
of macroeconomic news announcements on interest rate and foreign
exchange futures markets, particularly in terms of price changes and
volatility. Both studies, among others, find that prices, such as stock
prices, react primarily within minutes after the release of new
information.

Recently, the world has witnessed the rise of the Internet
which revolutionized the dissemination and accessibility of information.
Social media enables investors, analysts or politicians to instantly
share their information, news or opinions. This led some studies to
focus on the communication dynamics of social platforms to predict
changes in the returns of financial assets (@dechoudhuryCanBlogCommunication2008 and 
@bartovCanTwitterHelp2018). In this context, the
impact of Trump’s tweets on various financial and macroeconomic
variables has been analysed by several studies, especially during his
first mandate. Using high-frequency financial data,
@gjerstadPresidentTrumpsTweets2021 found consistent increases in uncertainty and
trading volume, along with a decline in the US stock market, regardless
of tweet content. It is relevant to note however, that the effect was stronger when 
Trump used confrontational words such as "tariff" or "trade war." Some of his
announcements also influenced the U.S. dollar exchange rate (@vlastakisInformationDemandStock2012)
and certain market indices within minutes of the tweet being posted
(@colonescuEffectsDonaldTrumps2018 and @kinyuaAnalysisImpactPresident2021).

Furthermore, scholars have shown that negative Trump tweets about specific
companies tended to reduce demand for their stocks (@bransHisThumbEffect2020 and
@mendelsStanfordResearchSeries2019), whereas some
others have shown that they also impact market volatility indices such as
the VIX (@fendelPoliticalNewsStock2019) or the Volfele (@klausMeasuringTrumpVolfefe2021).
The effects of his tweets also extended beyond the US. For example,
@nishimuraImpactsDonaldTrumps2025 show a
positive relationship between volatility in European stock markets and
Twitter activity of Trump, and this effect tends to intensify as public
interest for his tweet grows.

Our paper is built as follows: Section 2 describes the data, their sources, and 
the several transformations applied. Section 3 focuses on ARMA-X models, describing 
both our methodology and results. Section 4 does the same, though for our VAR models. 
Section 5 concludes and importantly Section 7 provides all the figures and tables.
