---
bibliography: macroeconometrics_citations.bib  #
csl: apa.csl
link-citations: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r, warning=FALSE, echo=FALSE, cache=TRUE}
require("here")
require("stringr")
require("dplyr")
require("ggplot2")
require("lubridate")

truths_raw <- read.csv(here("data/mothership", "social.csv"))

truths <- truths_raw %>%
  mutate(
    # Use POSIX 'timestamp' directly
    date_time_parsed = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S"),
    
    # Extract date only for plot
    day = as.Date(date_time_parsed),
    
    # Extract time only for plot
    time = format(date_time_parsed, "%H:%M"),
    
    # Convert time to numeric hours & minutes as fractions
    time_numeric = hour(date_time_parsed) + minute(date_time_parsed) / 60,
    
    # Shift time such that y = 0 corresponds to 12 PM
    time_shifted = time_numeric - 12
  )

```

# Introduction

## Motivation

Over the past 15 years social media has become an important
communication tool for politicians. One of the pioneers of this novel
approach has been Donald Trump, the 45th and 47th President of the United
States. Since his ban on Twitter after the January 6th riots, his quantity of
social media posts has drastically increased. This is shown in the following
figure. [^1]

[^1]: Includes both Posts and Reposts

The content of his posts can sometimes have announcements or teases of future
political decisions. Note the recent infamous "THIS IS A GREAT TIME TO BUY!!! DJT"
post sent just an hour before lifting his reciprocal tariffs. It is then not 
improbable that agents in financial markets might take this information into 
account in their decision making. This question has been asked before in the 
literature, focusing rather on his first term. 

This brings us to our research question:  Do Donald Trumps Posts impact market Volatility?

    
\@ref(fig:fig1)

```{r fig1, echo=FALSE, fig.cap="Terminally Online: Trump's Twitter & Truth Social Posts (EDT)", warning=FALSE, cache=TRUE}
 #Create the scatter plot
ggplot(truths, aes(x = day, y = time_shifted)) +
  geom_point(alpha = 0.5, color = "blue", size = 0.55) +  # Transparancy to create "heatmap"
  scale_y_continuous(
    breaks = seq(-12, 12, by = 3),  # Custom Y scale
    labels = c("00:00", "03:00", "06:00", "09:00", "12:00", "15:00", "18:00", "21:00", "24:00")  # 24-hour format labels
  ) +
  labs(title = "Terminally Online: Trumps Twitter & Truth Social Posts (EDT)",
       x = "",
       y = "Time of Day") +
  theme_minimal() +
  
  
  # Customize X Axis
  scale_x_date(
    date_labels = "%b %Y",  # Format labels to show month and year
    date_breaks = "9 months"
  ) +
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  
  # Add vertical lines at 9:30 AM and 4:00 PM for stock market
  geom_hline(yintercept = (9 + 30 / 60) - 12, linetype = "longdash", color = "red") + 
  geom_hline(yintercept = 16 - 12, linetype = "dashed", color = "red") +   
  
  # theme adjustments
  theme(
    panel.grid.minor = element_blank(),  # Remove minor gridlines
    panel.grid.major = element_line(linewidth = 0.5),  # Major gridlines
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )
```



## Literature Review

Information is one of the most valuable assets in the financial market.
Its importance lies at the core of the "Efficient Market Hypothesis", 
which states that the prices of assets fully reflect all
available information, adjusting immediately to any new data
(@famaAdjustmentStockPrices2003) , and thereby creating a strong demand
for information flow. In addition, the “Mixture of Distribution
Hypothesis” states that the release of new information is closely linked
to movements in both realized and implied volatility
(@andersenReturnVolatilityTrading1996, @frenchStockReturnVariances1986,
@vlastakisInformationDemandStock2012).

Consequently, a large part of the literature had focused on the relation
between announcements, news and market activity. For example,
@schumakerTextualAnalysisStock2009 use various linguistic and textual
representations derived from financial news to predict stock market
prices. Similarly, @ederingtonHowMarketsProcess1993 analyze the impact
of macroeconomic news announcements on interest rate and foreign
exchange futures markets, particularly in terms of price changes and
volatility. Both studies, among others, find that prices— such as stock
prices—react primarily within minutes after the release of new
information.

Recently, the world has witnessed the rise of the Internet
which revolutionized the dissemination and accessibility of information.
Social media enable investors, analysts or politicians to instantly
share their information, news or opinions. This led some studies to
focus on the communication dynamics of social platform to predict
changes in the returns of financial assets (@dechoudhuryCanBlogCommunication2008,
@bartovCanTwitterHelp2018). In this context, the
impact of Trump’s tweets on various financial and macroeconomic
variables has been analysed by several studies, especially during his
first mandate.

Using high-frequency financial data,
@gjerstadPresidentTrumpsTweets2021 found an increase in uncertainty and
trading volume, along with a decline in the U.S. stock market—regardless
of the tweet's content. However, the effect was stronger when Trump used
confrontational words such as "tariff" or "trade war." Some of his
announcements also influenced the U.S. dollar exchange rate (@vlastakisInformationDemandStock2012)
and certain market indices within minutes of the tweet being posted(
@colonescuEffectsDonaldTrumps2018 & @kinyuaAnalysisImpactPresident2021).

Other scholars have shown that negative Trump tweets about specific
companies tended to reduce demand for their stocks (@bransHisThumbEffect2020,
@mendelsStanfordResearchSeries2019), whereas some
other have shown that they also impact market volatility indices such as
the VIX (@fendelPoliticalNewsStock2019) or the Volfele (@klausMeasuringTrumpVolfefe2021).
The effects of his tweets also extended beyond the U.S.. For example,
@nishimuraImpactsDonaldTrumps2025 shows a
positive relationship between volatility in European stock markets and
tweeter activity of Trump, and this effect tends to intensify as public
intention for his tweet grows.

Our paper is built as follows: Section 2 describes the data, their sources, and 
the several transformations applied. Section 3 focuses on ARMA-X models, describing 
both our methodology and results. Section 4 does the same, though for our VAR models. 
Section 5 concludes.
