---
bibliography: macroeconometrics_citations.bib  #
csl: apa.csl
link-citations: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r, warning=FALSE, echo=FALSE}
require("here")
require("stringr")
require("dplyr")
require("ggplot2")
require("lubridate")

truths_raw <- read.csv(here("data/mothership", "social.csv"))

truths <- truths_raw %>%
  mutate(
    # Use POSIX 'timestamp' directly
    date_time_parsed = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S"),
    
    # Extract date only for plot
    day = as.Date(date_time_parsed),
    
    # Extract time only for plot
    time = format(date_time_parsed, "%H:%M"),
    
    # Convert time to numeric hours & minutes as fractions
    time_numeric = hour(date_time_parsed) + minute(date_time_parsed) / 60,
    
    # Shift time such that y = 0 corresponds to 12 PM
    time_shifted = time_numeric - 12
  )

```

# Introduction

Over the past 15 years social media has become an important
communications tool for politicians. One of the pioneers of this novel
approach has been Donald Trump, the 45th and 47th Presiden of the United
States. While he has been posting a lot online, he has increased posting
enourmously since he was banned from twitter after the Jan 6th riots.
This is on his own social media platform. As shown below he as been
posting constantly. [^1]

[^1]: Includes both Posts and Reposts

Especially in his second term he has been active on Truth Social for
long periods of time, often announcing or teasing important political
decision on there. Especially his announcement of "Now is a good time to
buy an hour before lifting reciprocal tariffs and him announcing his
post important Truth Social Post before Posting about price controls
lend to the fact that this has now become a major source of information.
Therefore the question wether financial markets react to these posts has
been discussed plenty. We investigate two research questions.

1)  Do Donald Trumps Posts impact market Volatility?
2)  Have traders learned from past actions and are now more reactive
    than they were during his first term?

```{r, warning=FALSE, echo=FALSE}
 #Create the scatter plot
ggplot(truths, aes(x = day, y = time_shifted)) +
  geom_point(alpha = 0.5, color = "blue", shape = ".") +  # Transparancy to create "heatmap"
  scale_y_continuous(
    breaks = seq(-12, 12, by = 3),  # Custom Y scale
    labels = c("00:00", "03:00", "06:00", "09:00", "12:00", "15:00", "18:00", "21:00", "24:00")  # 24-hour format labels
  ) +
  labs(title = "Terminally Online: Trumps Twitter & Truth Social Posts (EDT)",
       x = "Date",
       y = "Time of Day") +
  theme_minimal() +
  
  
  # Customize X Axis
  scale_x_date(
    date_labels = "%b %Y",  # Format labels to show month and year
    date_breaks = "9 months"
  ) +
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  
  # Add vertical lines at 9:30 AM and 4:00 PM for stock market
  geom_hline(yintercept = (9 + 30 / 60) - 12, linetype = "longdash", color = "red") + 
  geom_hline(yintercept = 16 - 12, linetype = "dashed", color = "red") +   
  
  # theme adjustments
  theme(
    panel.grid.minor = element_blank(),  # Remove minor gridlines
    panel.grid.major = element_line(linewidth = 0.5),  # Major gridlines
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )
```

## Literature Review

Information is one of the most valuable assets in the financial market.
Its importance lies at the core of the “Perfect Market Hypothesis”
(PMH), which states that the prices of assets fully reflect all
available information, adjusting immediately to any new data
@famaAdjustmentStockPrices2003 , and thereby creating a strong demand
for information flow. In addition, the “Mixture of Distribution
Hypothesis” states that the release of new information is closely linked
to movements in both realized and implied volatility (1)(3)(7).
Consequently, a large part of the literature had focused on the relation
between announcements, news and market activity. For example,
@schumakerTextualAnalysisStock2009 use various linguistic and textual
representations derived from financial news to predict stock market
prices. Similarly, @ederingtonHowMarketsProcess1993 analyze the impact
of macroeconomic news announcements on interest rate and foreign
exchange futures markets, particularly in terms of price changes and
volatility. Both studies, among others, find that prices— such as stock
prices—react primarily within minutes after the release of new
information. Recently, the world has witnessed the rise of the Internet
which revolutionized the dissemination and accessibility of information.
Social media enable investors, analysts or politicians to instantly
share their information, news or opinions. This led some studies to
focus on the communication dynamics of social platform to predict
changes in the returns of financial assets (6)(8). In this context, the
impact of Trump’s tweets on various financial and macroeconomic
variables has been analysed by several studies, especially during his
first mandate. Using high-frequency financial data,
@gjerstadPresidentTrumpsTweets2021 found an increase in uncertainty and
trading volume, along with a decline in the U.S. stock market—regardless
of the tweet's content. However, the effect was stronger when Trump used
confrontational words such as "tariff" or "trade war." Some of his
announcements also influenced the U.S. dollar exchange rate (l) and
certain market indices within minutes of the tweet being posted (r)(a).
Other scholars have shown that negative Trump’s tweets about specific
companies tended to reduce demand for their stocks (b)(g), whereas some
other have shown that they also impact market volatility indices such as
the VIX (w) or the Volfele(v). The effects of his tweets also extended
beyond the U.S.. For example, @nishimuraImpactsDonaldTrumps2025 shows a
positive relationship between volatility in European stock markets and
tweeter activity of Trump, and this effect tends to intensify as public
intention for his tweet grows (z).
