# Appendix


```{r library_setup_appendix, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE, cache=TRUE}
rm(list=ls())
# Core utilities
require(tinytex)       # LaTeX
require(here)          # Directory finder
require(stringr)       # String analysis
require(dplyr)         # Data manipulation
require(lubridate)     # Date handling
require(zoo)           # Time series lags
require(vroom)         # Fast data import
require(data.table)    # Efficient data filtering
require(tibble)        # Tidy data frames
require(tidyverse)     # Includes ggplot2, dplyr, etc.
require(knitr)         # Knitting reports
require(purrr)         # Functional programming

# Time series and econometrics
require(forecast)      # Time series models
require(expm)          # Matrix exponentials
require(AER)           # Applied Econometrics with R
require(AEC)           # JP-Renne functions
require(lmtest)        # Regression diagnostics
require(sandwich)      # Robust errors
require(sysid)         # ARMAX modeling
require(aTSA)          # ADF test
require(tseries)       # Time series tests
require(TSA)           # Time Series Analysis
require(vars)          # VAR models
require(quantmod)      # Quantitative financial modeling
require(FinTS)         # Financial time series
require(fGarch)        # GARCH models
require(rugarch)       # Univariate GARCH
require(rmgarch)       # Multivariate GARCH

# Text analysis
require(tidytext)      # Text mining
require(textstem)      # Lemmatization
require(quanteda)      # Tokenization
require(syuzhet)       # Sentiment analysis

# Table and reporting
require(jtools)        # Regression tables
require(huxtable)      # HTML/PDF tables
require(stargazer)     # Regression summary tables
require(texreg)        # LaTeX/HTML model output
require(kableExtra)    # Pretty tables in knitr

# Other
require(writexl)       # Write Excel files
require(alphavantager) # Alpha Vantage API access

#-> sorted with AI

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
source(here("helperfunctions/truths_cleaning_function.R"))
source(here("helperfunctions/armax_functions.R"))

```

## ARMAX

We choose the specification in the armax_models file. In this file, we will
just run said specifications to produce nice tables and graphs to include in 
our final paper. This is also why there are specification differences in the 
separate timeframes. We always use the best fit we found earlier.

```{r datasetup_appendix, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE, cache=TRUE}

#load final dataset
source(here("helperfunctions/full_data.R"))

#backup
backup = data

#select timeframe 
data = filter(data,between(timestamp, as.Date('2014-01-01'), as.Date('2025-05-07')))

#for interpretation
mean1 = mean(data$SPY_vol)

```


```{r fitting models, results=F, warning=F, message=F, echo=FALSE, cache=TRUE}
#All SPY models for the full Dataframe

models <- list()

# ARMA-X(3,3,1) with Tweet Dummy as Exogenous
models[["Model 1"]] <- armax(data$SPY_vol, xreg = data$dummy, latex = F,
                             nb.lags = 1, p = 3, q = 3) 

# ARMA-X(3,3,1) with Tweet Count as Exogenous
models[["Model 2"]] <- armax(data$SPY_vol, xreg = data$N, latex = F,
                             nb.lags = 1, p = 3, q = 3) 

# ARMA-X(3,2,3) with Tariff Mentions as Exogenous
models[["Model 3"]] <- armax(data$SPY_vol, xreg = data$tariff, latex = F,
                             nb.lags = 3, p = 3, q = 2) 

# ARMA-X(3,2,1) with Trade Mentions as Exogenous
models[["Model 4"]] <- armax(data$SPY_vol, xreg = data$trade, latex = F,
                             nb.lags = 1, p = 3, q = 2) 

# ARMA-X(3,2,0) with China Mentions as Exogenous
models[["Model 5"]] <- armax(data$SPY_vol, xreg = data$china, latex = F,
                             nb.lags = 0, p = 3, q = 2) 

```

### SPY ARMAX Table (Jan 2014 - May 2025) {#sec:spy-table}
```{r armaxfull, results="asis", warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
library(texreg)

# Define variable display names (HTML-friendly using <sub>)
names <- list(
  "ar1" = "AR(1)",
  "ar2" = "AR(2)",
  "ar3" = "AR(3)",
  "ma1" = "MA(1)",
  "ma2" = "MA(2)",
  "ma3" = "MA(3)",
  "(Intercept)" = "Constant",
  "dummy_lag_0" = "TweetDummy<sub>t</sub>",
  "dummy_lag_1" = "TweetDummy<sub>t-1</sub>",
  "N_lag_0" = "TweetCount<sub>t</sub>",
  "N_lag_1" = "TweetCount<sub>t-1</sub>",
  "tariff_lag_0" = "Tariff<sub>t</sub>",
  "tariff_lag_1" = "Tariff<sub>t-1</sub>",
  "tariff_lag_2" = "Tariff<sub>t-2</sub>",
  "tariff_lag_3" = "Tariff<sub>t-3</sub>",
  "trade_lag_0" = "Trade<sub>t</sub>",
  "trade_lag_1" = "Trade<sub>t-1</sub>",
  "china_lag_0" = "China<sub>t</sub>"
)

# Output the HTML table directly
cat(
  htmlreg(
    models,
    custom.model.names = names(models),
    custom.coef.map = names,
    caption = "ARMAX Models of Average Hourly Volatility",
    caption.above = TRUE,
    digits = 4,
    doctype = FALSE
  ))

```


### SPY ARMAX IRFs (Jan 2014 - May 2025){#sec:SPY-IRF}

```{r SPYirf, results="asis", warning=F, message=F, echo=FALSE, cache=TRUE}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

#irf.plot(models[["Model 1"]],nb.periods,title="Tweet Dummy Shock")
#irf.plot(models[["Model 2"]],nb.periods,title="Tweet Count Shock")
plot1 = irf.plot(models[["Model 3"]],nb.periods,
                 title="Tariff Mention Shock - Jan 2014 - May 2025")
plot1
#irf.plot(models[["Model 4"]],nb.periods,title="Trade Mention Shock")
#irf.plot(models[["Model 5"]],nb.periods,title="China Mention Shock")

ggsave("armax_plot1.png",plot=plot1,bg="white")

```


```{r, warning=F, message=F, echo=FALSE, results=F}
#Calculate residuals

res1 = checkresiduals(models[["Model 1"]], plot = FALSE)
res2 = checkresiduals(models[["Model 2"]], plot = FALSE)
res3 = checkresiduals(models[["Model 3"]], plot = FALSE)
res4 = checkresiduals(models[["Model 4"]], plot = FALSE)
res5 = checkresiduals(models[["Model 5"]], plot = FALSE)

```

```{r SPYres, warning=F, message=F, echo=FALSE, cache=TRUE}

resnames = c("Twitter Dummy", "Twitter Count", "Tariff", "Trade", "China")

#extract p-values directly from checkresiduals results
pvals <- data.frame("X-Regressor" = resnames,
                    `Full Timeframe` = c(
                      res1$p.value,
                      res2$p.value,
                      res3$p.value,
                      res4$p.value,
                      res5$p.value))


```




```{r datasetup first, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE, cache=TRUE}
#First term Calculations

#load final dataset
data = backup

#first term
data = filter(data,between(timestamp, as.Date('2017-01-20'), as.Date('2021-01-20')))

#for interpretation
mean2 = mean(data$SPY_vol)

```


```{r 1st term models, results=F, warning=F, message=F, echo=FALSE, cache=TRUE}
#SPY Models first Term

models <- list()

# ARMA-X(3,3,0) with Tariff Mentions as Exogenous
models[["First Term (1)"]] <- armax(data$SPY_vol, xreg = data$tariff, latex = F,
                             nb.lags = 0, p = 3, q = 3) 

# ARMA-X(3,3,0) with Trade Mentions as Exogenous
models[["First Term (2)"]] <- armax(data$SPY_vol, xreg = data$trade, latex = F,
                             nb.lags = 0, p = 3, q = 3)

# ARMA-X(3,3,0) with Trade Mentions as Exogenous
models[["First Term (3)"]] <- armax(data$SPY_vol, xreg = data$china, latex = F,
                             nb.lags = 0, p = 3, q = 3) 

```


```{r 1st SPYresiduals, warning=F, message=F, results=F, echo=FALSE, cache=TRUE}
# Run first term residuals
res6 = checkresiduals(models[["First Term (1)"]], plot = FALSE)
res7 = checkresiduals(models[["First Term (2)"]], plot = FALSE)
res8 = checkresiduals(models[["First Term (3)"]], plot = FALSE)

pvals_new1 <- data.frame(
  "First-Term" = c(
    NA,
    NA,
    res6$p.value,
    res7$p.value,
    res8$p.value))

```




```{r datasetup second, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE, cache=TRUE}
#Second Term Calculations

#load final dataset
data = backup

#second term
data = filter(data,between(timestamp, as.Date('2025-01-20'), as.Date('2025-05-07')))

#for interpretation
mean3 = mean(data$SPY_vol)

```


```{r 2nd term models, results=F, warning=F, message=F, echo=FALSE, cache=TRUE}
#Run Second Term Models

# ARMA-X(3,2,3) with Tariff Mentions as Exogenous
models[["Second Term (1)"]] <- armax(data$SPY_vol, xreg = data$tariff, latex = F,
                             nb.lags = 2, p = 1, q = 2) 

# ARMA-X(3,2,1) with Trade Mentions as Exogenous
models[["Second Term (2)"]] <- armax(data$SPY_vol, xreg = data$trade, latex = F,
                             nb.lags = 0, p = 1, q = 2) 

# ARMA-X(3,2,0) with China Mentions as Exogenous
models[["Second Term (3)"]] <- armax(data$SPY_vol, xreg = data$china, latex = F,
                             nb.lags = 2, p = 1, q = 2) 

```



```{r 2nd SPYresiduals, results=F, warning=F, message=F, echo=FALSE, cache=TRUE}
# Calculate SPY residuals for the second term

res9 = checkresiduals(models[["Second Term (1)"]], plot = FALSE)
res10 = checkresiduals(models[["Second Term (2)"]], plot = FALSE)
res11 = checkresiduals(models[["Second Term (3)"]], plot = FALSE)

pvals_new2 <- data.frame(
  "Second-Term" = c(
    NA,
    NA,
    res9$p.value,
    res10$p.value,
    res11$p.value))

#combine with other term
pvals_combined <- cbind(pvals,pvals_new1)
pvals_combined <- cbind(pvals_combined, pvals_new2)

```


### SPY ARMAX Table (Split Presidential Terms){#sec:spy-table-terms}

\centering

```{r armax1, results="asis", warning=F, echo=FALSE, message=F, cache=TRUE}

library(texreg)

# Change model names (not sure if needed anymore)
model_names <- c(
 "First Term (1)", "First Term (2)", "First Term (3)",
 "Second Term (1)", "Second Term (2)", "Second Term (3)"
)
names(models) <- model_names

# HTML coefficients names adjusted (is this correct?)
xnames_ordered <- c(
  "AR(1)", "AR(2)", "AR(3)",
  "MA(1)", "MA(2)", "MA(3)",
  "Constant",
  "Tariff<sub>t</sub>", "Tariff<sub>t-1</sub>", "Tariff<sub>t-2</sub>",
  "Trade<sub>t</sub>",
  "China<sub>t</sub>", "China<sub>t-1</sub>", "China<sub>t-2</sub>"
)

# Render as html -> need to render file to have it nice
htmlreg(
  models,
  custom.coef.names = xnames_ordered,
  custom.model.names = model_names,
  caption = "Split-Term ARMAX Models of Average Hourly Volatility",
  caption.above = TRUE,
  digits = 4,
  stars = c(0.001, 0.01, 0.05),
  doctype = FALSE)


```


### SPY ARMAX IRFs (Split Terms){#sec:SPY-SPLIT-IRF}

```{r 2nd SPYirf, warning=F, message=F, echo=FALSE, cache=TRUE}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

plot2 = irf.plot(models[["Second Term (1)"]],nb.periods,
                 title="Tariff Mention Shock - Second Term")
plot2

#ggsave("armax_plot2.png",plot=plot2,bg="white")

plot3 = irf.plot(models[["Second Term (3)"]],nb.periods,
                 title="China Mention Shock - Second Term")
plot3

#ggsave("armax_plot3.png",plot=plot3,bg="white")

```


### Residual Test {#sec:SPY-res-test}

```{r res-table, message=F, warning=F, results="asis", echo=FALSE, cache=TRUE}

kable(pvals_combined, digits = 6, format="html", caption = "Ljung-Box Test p-values for Residuals") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE, position = "center")



```

### Descriptive Stats{#sec:means-table}
 
```{r means, message=F, warning=F, results="asis", cache=TRUE}

means <- data.frame(
  Model = c("Full Time Mean", "First Term Mean", "Second Term Mean"),
  `SPY Volatility Mean` = c(
    mean1,
    mean2,
    mean3))

kable(means, digits = 6, format="html", caption = "Summary Statistics of SPY Volatility") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE, position = "center")



```

## VAR

```{r load_data_var, message=FALSE, warning=FALSE, results=FALSE, echo=FALSE}
#select timeframe 
Vdata = filter(data,between(timestamp, as.Date('2014-01-01'), as.Date('2025-05-07')))
```

```{r Estime dummy, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Dummy Estimates
#-------------------------

y = cbind(Vdata$dummy, Vdata$SPY_vol)
colnames(y)[1:2] <- c("dummy", "vol")
est.VAR <- VAR(y,p=6)

#extract results
mod_vol = est.VAR$varresult$vol
f = formula(mod_vol)
d = model.frame(mod_vol)
lm_clean = lm(f, data= d)

#apply Newey-West
nw_vcov = NeweyWest(lm_clean, lag=6)
nw_se = sqrt(diag(nw_vcov))

#t-stats
coef = coef(lm_clean)
t_stat = coef/nw_se

#recalculate p-values
robust = 2*(1-pt(abs(t_stat), df = df.residual(lm_clean)))
```

```{r B mat, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
#Recreate a Robust Omega Matrix
U = residuals(est.VAR)
T = nrow(U)
L = 6 #number of lag
Omega = matrix(0, ncol(U), ncol(U))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l_ = t(U[(l+1):T, , drop=FALSE]) %*% U[1:(T-l), , drop=FALSE] /T
  if (l == 0){
    Omega = Omega + Gamma_l_
  } else {
    Omega = Omega + weight*(Gamma_l_ + t(Gamma_l_))
  }
}

#make the B matrix
loss <- function(param){
  #Define the restriction
  B <- matrix(c(param[1], param[2], 0, param[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X <- Omega - B %*% t(B)
  
  #loss function
  loss <- sum(X^2)
  return(loss)
}

res.opt <- optim(c(1, 0, 1), loss, method = "BFGS")
B.hat <- matrix(c(res.opt$par[1], res.opt$par[2], 0, res.opt$par[3]), ncol = 2)
```

### Full Timeframe IRF Tweet Dummy

```{r IRF 1dummy, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
nb.sim = 7*7
#get back the coefficient of est.VAR
phi <- Acoef(est.VAR)
PHI = make.PHI(phi)

#take the constant
constant <- sapply(est.VAR$varresult, function(eq) coef(eq)["const"])
c=as.matrix(constant)

#Simulate the IRF
p <- length(phi)
n <- dim(phi[[1]])[1]


Y <- simul.VAR(c=c, Phi = phi, B = B.hat, nb.sim ,y0.star=rep(0, n*p),
                  indic.IRF = 1, u.shock = c(1,0))



Yd = data.frame(
  period = 1:nrow(Y),
  response = Y[,2])

ggplot(Yd,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of Dummy on Volatility")+
  ylab("")+
  xlab("") +
  theme_minimal()

```

### Cumultative IRF of Dummy Full term

```{r IRF 2Dummy, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
ggplot(Yd,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of Dummy on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

```{r estimate with N, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
y2 = cbind(Vdata$N, Vdata$SPY_vol)
colnames(y2)[1:2] <- c("N", "vol")
est.VAR2 <- VAR(y2,p=6)

#extract results
mod_vol2 = est.VAR2$varresult$vol
f2 = formula(mod_vol2)
d2 = model.frame(mod_vol2)
lm_clean2 = lm(f2, data= d2)

#apply Newey-West
nw_vcov2 = NeweyWest(lm_clean2, lag=6)
nw_se2 = sqrt(diag(nw_vcov2))

#t-stats
coef2 = coef(lm_clean2)
t_stat2 = coef2/nw_se2

#recalculate p-values
robust2 = 2*(1-pt(abs(t_stat2), df = df.residual(lm_clean2)))

```

```{r estime tariff, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Tariff Estimates
#---------------------
y3 = cbind(Vdata$tariff, Vdata$SPY_vol)
colnames(y3)[1:2] <- c("tariff", "vol")
est.VAR3 <- VAR(y3,p=6)

#extract results
mod_vol3 = est.VAR3$varresult$vol
f3 = formula(mod_vol3)
d3 = model.frame(mod_vol3)
lm_clean3 = lm(f3, data= d3)

#apply Newey-West
nw_vcov3 = NeweyWest(lm_clean3, lag=6)
nw_se3 = sqrt(diag(nw_vcov3))

#t-stats
coef3 = coef(lm_clean3)
t_stat3 = coef3/nw_se3

#recalculate p-values
robust3 = 2*(1-pt(abs(t_stat3), df = df.residual(lm_clean3)))

```

```{r B mat3, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
#Recreate a Robust Omega Matrix
U3 = residuals(est.VAR3)
T3 = nrow(U3)
Omega3 = matrix(0, ncol(U3), ncol(U3))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l_3 = t(U3[(l+1):T3, , drop=FALSE]) %*% U3[1:(T3-l), , drop=FALSE] /T3
  if (l == 0){
    Omega3 = Omega3 + Gamma_l_3
  } else {
    Omega3 = Omega3 + weight*(Gamma_l_3 + t(Gamma_l_3))
  }
}


#make the B matrix
loss3 <- function(param3){
  #Define the restriction
  B3 <- matrix(c(param3[1], param3[2], 0, param3[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X3 <- Omega3 - B3 %*% t(B3)
  
  #loss function
  loss3 <- sum(X3^2)
  return(loss3)
}

res.opt3 <- optim(c(1, 0, 1), loss3, method = "BFGS")
B.hat3 <- matrix(c(res.opt3$par[1], res.opt3$par[2], 0, res.opt3$par[3]), ncol = 2)



```

### IRF Tariff full Timeframe

```{r IRF tariffff, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
#get back the coefficient of est.VAR
phi3 <- Acoef(est.VAR3)
PHI3 = make.PHI(phi3)

#take the constant
constant3 <- sapply(est.VAR3$varresult, function(eq) coef(eq)["const"])
c3=as.matrix(constant3)

#Simulate the IRF
p3 <- length(phi3)
n3 <- dim(phi3[[1]])[1]

Y3 <- simul.VAR(c=c3, Phi = phi3, B = B.hat3, nb.sim ,y0.star=rep(0, n3*p3),
                  indic.IRF = 1, u.shock = c(1,0))


#Plot the IRF
Yd3 = data.frame(
  period = 1:nrow(Y3),
  response = Y3[,2])

ggplot(Yd3,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of tariff on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

### IRF Tariff Cumultative

```{r IRF tariff, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
ggplot(Yd3,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of tariff on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```


```{r estimate trade, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Trade Estimates
#----------------------

y4 = cbind(Vdata$trade, Vdata$SPY_vol)
colnames(y4)[1:2] <- c("trade", "vol")
est.VAR4 <- VAR(y4,p=6)

#extract results
mod_vol4 = est.VAR4$varresult$vol
f4 = formula(mod_vol4)
d4 = model.frame(mod_vol4)
lm_clean4 = lm(f4, data= d4)

#apply Newey-West
nw_vcov4 = NeweyWest(lm_clean4, lag=6)
nw_se4 = sqrt(diag(nw_vcov4))

#t-stats
coef4 = coef(lm_clean4)
t_stat4 = coef4/nw_se4

#recalculate p-values
robust4 = 2*(1-pt(abs(t_stat4), df = df.residual(lm_clean4)))


```

```{r estime China, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Chinae Estimates
#---------------------
ychina = cbind(Vdata$china, Vdata$SPY_vol)
colnames(ychina)[1:2] <- c("china", "vol")
est.VARchina <- VAR(ychina,p=6)

#extract results
mod_volchina = est.VARchina$varresult$vol
fchina = formula(mod_volchina)
dchina = model.frame(mod_volchina)
lm_cleanchina = lm(fchina, data= dchina)

#apply Newey-West
nw_vcovchina = NeweyWest(lm_cleanchina, lag=6)
nw_sechina = sqrt(diag(nw_vcovchina))

#t-stats
coefchina = coef(lm_cleanchina)
t_statchina = coefchina/nw_sechina

#recalculate p-values
robustchina = 2*(1-pt(abs(t_statchina), df = df.residual(lm_cleanchina)))
```

### Table 1 VAR results='asis'

```{r mana, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
dt_t = d %>%
    rename(X.l1 = dummy.l1,
    X.l2 = dummy.l2,
    X.l3 = dummy.l3,
    X.l4 = dummy.l4,
    X.l5 = dummy.l5,
    X.l6 = dummy.l6)


f_t <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model <- lm(f_t, data = dt_t)

dt_t2 = d2 %>%
    rename(X.l1 = N.l1,
    X.l2 = N.l2,
    X.l3 = N.l3,
    X.l4 = N.l4,
    X.l5 = N.l5,
    X.l6 = N.l6)



f_t2 <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model2 <- lm(f_t2, data = dt_t2)


dt_t3 = d3 %>%
    rename(X.l1 = tariff.l1,
    X.l2 = tariff.l2,
    X.l3 = tariff.l3,
    X.l4 = tariff.l4,
    X.l5 = tariff.l5,
    X.l6 = tariff.l6)



f_t3 <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model3 <- lm(f_t3, data = dt_t3)


dt_t4 = d4 %>%
    rename(X.l1 = trade.l1,
    X.l2 = trade.l2,
    X.l3 = trade.l3,
    X.l4 = trade.l4,
    X.l5 = trade.l5,
    X.l6 = trade.l6)
  


f_t4 <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model4 <- lm(f_t4, data = dt_t4)

dt_tchina = dchina %>%
    rename(X.l1 = china.l1,
    X.l2 = china.l2,
    X.l3 = china.l3,
    X.l4 = china.l4,
    X.l5 = china.l5,
    X.l6 = china.l6)



f_tchina <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
modelchina <- lm(f_tchina, data = dt_tchina)


nw_se_t <- sqrt(diag(sandwich::NeweyWest(model, lag = 6)))
nw_se2_t <- sqrt(diag(sandwich::NeweyWest(model2, lag = 6)))
nw_se3_t <- sqrt(diag(sandwich::NeweyWest(model3, lag = 6)))
nw_se4_t <- sqrt(diag(sandwich::NeweyWest(model4, lag = 6)))
nw_sechina_t <- sqrt(diag(sandwich::NeweyWest(modelchina, lag = 6)))


robust_t <- 2 * (1-pt(abs(coef(model) / nw_se_t), df = df.residual(model)))
robust2_t <- 2 * (1-pt(abs(coef(model2) / nw_se2_t), df = df.residual(model2)))
robust3_t <- 2 * (1-pt(abs(coef(model3) / nw_se3_t), df = df.residual(model3)))
robust4_t <- 2 * (1-pt(abs(coef(model4) / nw_se4_t), df = df.residual(model4)))
robustchina_t <- 2 * (1-pt(abs(coef(modelchina) / nw_sechina_t), df = df.residual(modelchina)))



nw_se_t       <- nw_se_t[names(coef(model))]
robust_t      <- robust_t[names(coef(model))]
nw_se2_t      <- nw_se2_t[names(coef(model2))]
robust2_t     <- robust2_t[names(coef(model2))]
nw_se3_t      <- nw_se3_t[names(coef(model3))]
robust3_t     <- robust3_t[names(coef(model3))]
nw_se4_t      <- nw_se4_t[names(coef(model4))]
robust4_t     <- robust4_t[names(coef(model4))]
nw_sechina_t  <- nw_sechina_t[names(coef(modelchina))]
robustchina_t <- robustchina_t[names(coef(modelchina))]




# Create list for models
models_list <- list(model, model2, model3, model4, modelchina)

# Create list for SE robustes
robust_ses <- list(nw_se_t, nw_se2_t, nw_se3_t, nw_se4_t, nw_sechina_t)

# Create list for p-value
robust_pvals <- list(robust_t, robust2_t, robust3_t, robust4_t, robustchina_t)

# Name of Variables
custom_names <- list(
  "vol.l1" = "$AHV_{t-1}$",
  "vol.l2" = "$AHV_{t-2}$",
  "vol.l3" = "$AHV_{t-3}$",
  "vol.l4" = "$AHV_{t-4}$",
  "vol.l5" = "$AHV_{t-5}$",
  "vol.l6" = "$AHV_{t-6}$",
  "X.l1" = "$X_{t-1}$",
  "X.l2" = "$X_{t-2}$",
  "X.l3" = "$X_{t-3}$",
  "X.l4" = "$X_{t-4}$",
  "X.l5" = "$X_{t-5}$",
  "X.l6" = "$X_{t-6}$",
  "const" = "Constant"
)
```
### html table

```{r, warning=FALSE, results='asis'}
tmpfile <- tempfile(fileext = ".html")  # create temp file

table_texreg_html <- htmlreg(
  l = models_list,
  override.se = robust_ses,
  override.pvalues = robust_pvals,
  custom.coef.map = custom_names,
  custom.model.names = c("TweetDummy", "TweetCount", "Tariff", "Trade", "China"),
  caption = "VAR Models of Average Hourly Volatility",
  digits = 6,
  custom.gof.rows = list("Shock (IRF)" = c(0.0041713, 0.003061, 0.001189, 0.000215, 0.001937)),
  custom.note = "This table displays VAR regression with only two variables: AHV and the X regressor. Column names represent the X variable for the selected model.",
  file = tmpfile
)

cat(readLines(tmpfile), sep = "\n")
```




```{r datasetup2, results=FALSE, warning=FALSE, message=FALSE, cache=TRUE, echo=FALSE}
data <- c(0)

source(here("helperfunctions/full_data.R"))



# First and Second Mandate

#first term
Vdata_f = filter(data,between(timestamp, as.Date('2017-01-20'), as.Date('2021-01-20')))

#second term
Vdata_s = filter(data,between(timestamp, as.Date('2025-01-20'), as.Date('2025-05-07')))

```


### Dummy First Term

```{r first mandate dum, warning=FALSE, message=FALSE, results="asis", cache=TRUE}
# First Term Estimates
#------------------------
# Dummy


y_f_d = cbind(Vdata_f$dummy, Vdata_f$SPY_vol)
colnames(y_f_d)[1:2] <- c("dummy", "vol")
est.VAR_f_d <- VAR(y_f_d,p=6)

#extract results
mod_vol_f_d = est.VAR_f_d$varresult$vol
f_f_d = formula(mod_vol_f_d)
d_f_d = model.frame(mod_vol_f_d)
lm_clean_f_d = lm(f_f_d, data= d_f_d)

#apply Newey-West
nw_vcov_f_d = NeweyWest(lm_clean_f_d, lag=6)
nw_se_f_d = sqrt(diag(nw_vcov_f_d))

#t-stats
coef_f_d = coef(lm_clean_f_d)
t_stat_f_d = coef_f_d/nw_se_f_d

#recalculate p-values
robust_f_d = 2*(1-pt(abs(t_stat_f_d), df = df.residual(lm_clean_f_d)))


```

### First Mandate

```{r first mandate N, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_f_n = cbind(Vdata_f$N, Vdata_f$SPY_vol)
colnames(y_f_n)[1:2] <- c("N", "vol")
est.VAR_f_n <- VAR(y_f_n,p=6)

#extract results
mod_vol_f_n = est.VAR_f_n$varresult$vol
f_f_n = formula(mod_vol_f_n)
d_f_n = model.frame(mod_vol_f_n)
lm_clean_f_n = lm(f_f_n, data= d_f_n)

#apply Newey-West
nw_vcov_f_n = NeweyWest(lm_clean_f_n, lag=6)
nw_se_f_n = sqrt(diag(nw_vcov_f_n))

#t-stats
coef_f_n = coef(lm_clean_f_n)
t_stat_f_n = coef_f_n/nw_se_f_n

#recalculate p-values
robust_f_n = 2*(1-pt(abs(t_stat_f_n), df = df.residual(lm_clean_f_n)))
```

### Tariff first Mandate

```{r first mandate tariff, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_f_ta = cbind(Vdata_f$tariff, Vdata_f$SPY_vol)
colnames(y_f_ta)[1:2] <- c("tariff", "vol")
est.VAR_f_ta <- VAR(y_f_ta,p=6)

#extract results
mod_vol_f_ta = est.VAR_f_ta$varresult$vol
f_f_ta = formula(mod_vol_f_ta)
d_f_ta = model.frame(mod_vol_f_ta)
lm_clean_f_ta = lm(f_f_ta, data= d_f_ta)

#apply Newey-West
nw_vcov_f_ta = NeweyWest(lm_clean_f_ta, lag=6)
nw_se_f_ta = sqrt(diag(nw_vcov_f_ta))

#t-stats
coef_f_ta = coef(lm_clean_f_ta)
t_stat_f_ta = coef_f_ta/nw_se_f_ta

#recalculate p-values
robust_f_ta = 2*(1-pt(abs(t_stat_f_ta), df = df.residual(lm_clean_f_ta)))

```

### Trade First Mandate

```{r first mandate trade, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_f_tr = cbind(Vdata_f$trade, Vdata_f$SPY_vol)
colnames(y_f_tr)[1:2] <- c("trade", "vol")
est.VAR_f_tr <- VAR(y_f_tr,p=6)

#extract results
mod_vol_f_tr = est.VAR_f_tr$varresult$vol
f_f_tr = formula(mod_vol_f_tr)
d_f_tr = model.frame(mod_vol_f_tr)
lm_clean_f_tr = lm(f_f_tr, data= d_f_tr)

#apply Newey-West
nw_vcov_f_tr = NeweyWest(lm_clean_f_tr, lag=6)
nw_se_f_tr = sqrt(diag(nw_vcov_f_tr))

#t-stats
coef_f_tr = coef(lm_clean_f_tr)
t_stat_f_tr = coef_f_tr/nw_se_f_tr

#recalculate p-values
robust_f_tr = 2*(1-pt(abs(t_stat_f_tr), df = df.residual(lm_clean_f_tr)))
```

### China First Mandate

```{r first mandate china, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_f_ch = cbind(Vdata_f$china, Vdata_f$SPY_vol)
colnames(y_f_ch)[1:2] <- c("china", "vol")
est.VAR_f_ch <- VAR(y_f_ch,p=6)

#extract results
mod_vol_f_ch = est.VAR_f_ch$varresult$vol
f_f_ch = formula(mod_vol_f_ch)
d_f_ch = model.frame(mod_vol_f_ch)
lm_clean_f_ch = lm(f_f_ch, data= d_f_ch)

#apply Newey-West
nw_vcov_f_ch = NeweyWest(lm_clean_f_ch, lag=6)
nw_se_f_ch = sqrt(diag(nw_vcov_f_ch))

#t-stats
coef_f_ch = coef(lm_clean_f_ch)
t_stat_f_ch = coef_f_ch/nw_se_f_ch

#recalculate p-values
robust_f_ch = 2*(1-pt(abs(t_stat_f_ch), df = df.residual(lm_clean_f_ch)))


```



### Second Term

### Dummy

```{r second mandate dum, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_s_d = cbind(Vdata_s$dummy, Vdata_s$SPY_vol)
colnames(y_s_d)[1:2] <- c("dummy", "vol")
est.VAR_s_d <- VAR(y_s_d,p=6)

#extract results
mod_vol_s_d = est.VAR_s_d$varresult$vol
f_s_d = formula(mod_vol_s_d)
d_s_d = model.frame(mod_vol_s_d)
lm_clean_s_d = lm(f_s_d, data= d_s_d)

#apply Newey-West
nw_vcov_s_d = NeweyWest(lm_clean_s_d, lag=6)
nw_se_s_d = sqrt(diag(nw_vcov_s_d))

#t-stats
coef_s_d = coef(lm_clean_s_d)
t_stat_s_d = coef_s_d/nw_se_s_d

#recalculate p-values
robust_s_d = 2*(1-pt(abs(t_stat_s_d), df = df.residual(lm_clean_s_d)))
```


### N 

```{r second mandate N, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_s_n = cbind(Vdata_s$N, Vdata_s$SPY_vol)
colnames(y_s_n)[1:2] <- c("N", "vol")
est.VAR_s_n <- VAR(y_s_n,p=6)

#extract results
mod_vol_s_n = est.VAR_s_n$varresult$vol
f_s_n = formula(mod_vol_s_n)
d_s_n = model.frame(mod_vol_s_n)
lm_clean_s_n = lm(f_s_n, data= d_s_n)

#apply Newey-West
nw_vcov_s_n = NeweyWest(lm_clean_s_n, lag=6)
nw_se_s_n = sqrt(diag(nw_vcov_s_n))

#t-stats
coef_s_n = coef(lm_clean_s_n)
t_stat_s_n = coef_s_n/nw_se_s_n

#recalculate p-values
robust_s_n = 2*(1-pt(abs(t_stat_s_n), df = df.residual(lm_clean_s_n)))


```

### Tariff

```{r second mandate tariff, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_s_ta = cbind(Vdata_s$tariff, Vdata_s$SPY_vol)
colnames(y_s_ta)[1:2] <- c("tariff", "vol")
est.VAR_s_ta <- VAR(y_s_ta,p=6)

#extract results
mod_vol_s_ta = est.VAR_s_ta$varresult$vol
f_s_ta = formula(mod_vol_s_ta)
d_s_ta = model.frame(mod_vol_s_ta)
lm_clean_s_ta = lm(f_s_ta, data= d_s_ta)

#apply Newey-West
nw_vcov_s_ta = NeweyWest(lm_clean_s_ta, lag=6)
nw_se_s_ta = sqrt(diag(nw_vcov_s_ta))

#t-stats
coef_s_ta = coef(lm_clean_s_ta)
t_stat_s_ta = coef_s_ta/nw_se_s_ta

#recalculate p-values
robust_s_ta = 2*(1-pt(abs(t_stat_s_ta), df = df.residual(lm_clean_s_ta)))

```

### Trade

```{r second mandate trade, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_s_tr = cbind(Vdata_s$trade, Vdata_s$SPY_vol)
colnames(y_s_tr)[1:2] <- c("trade", "vol")
est.VAR_s_tr <- VAR(y_s_tr,p=6)

#extract results
mod_vol_s_tr = est.VAR_s_tr$varresult$vol
f_s_tr = formula(mod_vol_s_tr)
d_s_tr = model.frame(mod_vol_s_tr)
lm_clean_s_tr = lm(f_s_tr, data= d_s_tr)

#apply Newey-West
nw_vcov_s_tr = NeweyWest(lm_clean_s_tr, lag=6)
nw_se_s_tr = sqrt(diag(nw_vcov_s_tr))

#t-stats
coef_s_tr = coef(lm_clean_s_tr)
t_stat_s_tr = coef_s_tr/nw_se_s_tr

#recalculate p-values
robust_s_tr = 2*(1-pt(abs(t_stat_s_tr), df = df.residual(lm_clean_s_tr)))

```

### China

```{r second mandate china, warning=FALSE, message=FALSE, results="asis", cache=TRUE}

y_s_ch = cbind(Vdata_s$china, Vdata_s$SPY_vol)
colnames(y_s_ch)[1:2] <- c("china", "vol")
est.VAR_s_ch <- VAR(y_s_ch,p=6)

#extract results
mod_vol_s_ch = est.VAR_s_ch$varresult$vol
f_s_ch = formula(mod_vol_s_ch)
d_s_ch = model.frame(mod_vol_s_ch)
lm_clean_s_ch = lm(f_s_ch, data= d_s_ch)

#apply Newey-West
nw_vcov_s_ch = NeweyWest(lm_clean_s_ch, lag=6)
nw_se_s_ch = sqrt(diag(nw_vcov_s_ch))

#t-stats
coef_s_ch = coef(lm_clean_s_ch)
t_stat_s_ch = coef_s_ch/nw_se_s_ch

#recalculate p-values
robust_s_ch = 2*(1-pt(abs(t_stat_s_ch), df = df.residual(lm_clean_s_ch)))

```

###

```{r B mat second mandate china, warning=FALSE, message=FALSE, cache=TRUE}
#Construct the Robust Omega Matrix
L <- 6
nb.sim = 7*7

U_s_ch = residuals(est.VAR_s_ch)
T_s_ch = nrow(U_s_ch)
Omega_s_ch = matrix(0, ncol(U_s_ch), ncol(U_s_ch))
for(l in 0:L) {
  weight = 1 - l/(L+1)
  Gamma_l__s_ch = t(U_s_ch[(l+1):T_s_ch, , drop=FALSE]) %*% U_s_ch[1:(T_s_ch-l), , drop=FALSE] /T_s_ch
  if (l == 0){
    Omega_s_ch = Omega_s_ch + Gamma_l__s_ch
  } else {
    Omega_s_ch = Omega_s_ch + weight*(Gamma_l__s_ch + t(Gamma_l__s_ch))
  }
}


#make the B matrix
loss_s_ch <- function(param_s_ch){
  #Define the restriction
  B_s_ch <- matrix(c(param_s_ch[1], param_s_ch[2], 0, param_s_ch[3]), ncol = 2)
  
  #Make BB' approximatively equal to omega
  X_s_ch <- Omega_s_ch - B_s_ch %*% t(B_s_ch)
  
  #loss function
  loss_s_ch <- sum(X_s_ch^2)
  return(loss_s_ch)
}

res.opt_s_ch <- optim(c(1, 0, 1), loss_s_ch, method = "BFGS")
B.hat_s_ch <- matrix(c(res.opt_s_ch$par[1], res.opt_s_ch$par[2], 0, res.opt_s_ch$par[3]), ncol = 2)



```

### IRF Second Term China

```{r IRF second china, warning=FALSE, message=FALSE, cache=TRUE}
#get back the coefficient of est.VAR
phi_s_ch <- Acoef(est.VAR_s_ch)
PHI_s_ch = make.PHI(phi_s_ch)

#take the constant
constant_s_ch <- sapply(est.VAR_s_ch$varresult, function(eq) coef(eq)["const"])
c_s_ch=as.matrix(constant_s_ch)

#Simulate the IRF
p_s_ch <- length(phi_s_ch)
n_s_ch <- dim(phi_s_ch[[1]])[1]

Y_s_ch <- simul.VAR(c=c_s_ch, Phi = phi_s_ch, B = B.hat_s_ch, nb.sim ,y0.star=rep(0, n_s_ch*p_s_ch),
                  indic.IRF = 1, u.shock = c(1,0))


#Plot the IRF
Yd_s_ch = data.frame(
  period = 1:nrow(Y_s_ch),
  response = Y_s_ch[,2])

ggplot(Yd_s_ch,aes(x=period, y=response)) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P IRF of Second Term China on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

## IRF Cumultative Second Term China
```{r IRF _s_ch, cache=TRUE}
ggplot(Yd_s_ch,aes(x=period, y=cumsum(response))) +
  geom_hline(yintercept = 0, color="red") +
  geom_line() +
  theme_light() +
  ggtitle("S&P Cumulalitve IRF of Second Term China on Volatility") +
  ylab("")+
  xlab("") +
  theme_minimal()
```

## Tables Terms

```{r table first term, message=FALSE, warning=FALSE, results='asis', cache=TRUE}


#first

d_f_d_t = d_f_d %>%
    rename(X.l1 = dummy.l1,
    X.l2 = dummy.l2,
    X.l3 = dummy.l3,
    X.l4 = dummy.l4,
    X.l5 = dummy.l5,
    X.l6 = dummy.l6)

f_t_f_d <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_f_d <- lm(f_t_f_d, data = d_f_d_t)

d_f_n_t = d_f_n %>%
    rename(X.l1 = N.l1,
    X.l2 = N.l2,
    X.l3 = N.l3,
    X.l4 = N.l4,
    X.l5 = N.l5,
    X.l6 = N.l6)

f_t_f_n <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_f_n <- lm(f_t_f_n, data = d_f_n_t)

d_f_ta_t = d_f_ta %>%
    rename(X.l1 = tariff.l1,
    X.l2 = tariff.l2,
    X.l3 = tariff.l3,
    X.l4 = tariff.l4,
    X.l5 = tariff.l5,
    X.l6 = tariff.l6)

f_t_f_ta <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_f_ta <- lm(f_t_f_ta, data = d_f_ta_t)


d_f_tr_t = d_f_tr %>%
    rename(X.l1 = trade.l1,
    X.l2 = trade.l2,
    X.l3 = trade.l3,
    X.l4 = trade.l4,
    X.l5 = trade.l5,
    X.l6 = trade.l6)

f_t_f_tr <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_f_tr <- lm(f_t_f_tr, data = d_f_tr_t)


d_f_ch_t = d_f_ch %>%
    rename(X.l1 = china.l1,
    X.l2 = china.l2,
    X.l3 = china.l3,
    X.l4 = china.l4,
    X.l5 = china.l5,
    X.l6 = china.l6)

f_t_f_ch <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_f_ch <- lm(f_t_f_ch, data = d_f_ch_t)




nw_se_f_d_t <- sqrt(diag(sandwich::NeweyWest(model_f_d, lag = 6)))
nw_se_f_n_t <- sqrt(diag(sandwich::NeweyWest(model_f_n, lag = 6)))
nw_se_f_ta_t <- sqrt(diag(sandwich::NeweyWest(model_f_ta, lag = 6)))
nw_se_f_tr_t <- sqrt(diag(sandwich::NeweyWest(model_f_tr, lag = 6)))
nw_se_f_china_t <- sqrt(diag(sandwich::NeweyWest(model_f_ch, lag = 6)))


robust_f_d_t <- 2 * (1-pt(abs(coef(model_f_d) / nw_se_f_d_t), df = df.residual(model_f_d)))
robust_f_n_t <- 2 * (1-pt(abs(coef(model_f_n) / nw_se_f_n_t), df = df.residual(model_f_n)))
robust_f_ta_t <- 2 * (1-pt(abs(coef(model_f_ta) / nw_se_f_ta_t), df = df.residual(model_f_ta)))
robust_f_tr_t <- 2 * (1-pt(abs(coef(model_f_tr) / nw_se_f_tr_t), df = df.residual(model_f_tr)))
robust_f_ch_t <- 2 * (1-pt(abs(coef(model_f_ch) / nw_se_f_china_t), df = df.residual(model_f_ch)))


nw_se_f_d_t       <- nw_se_f_d_t[names(coef(model_f_d))]
robust_f_d_t      <- robust_f_d_t[names(coef(model_f_d))]
nw_se_f_n_t      <- nw_se_f_n_t[names(coef(model_f_n))]
robust_f_n_t     <- robust_f_n_t[names(coef(model_f_n))]
nw_se_f_ta_t      <- nw_se_f_ta_t[names(coef(model_f_ta))]
robust_f_ta_t     <- robust_f_ta_t[names(coef(model_f_ta))]
nw_se_f_tr_t     <- nw_se_f_tr_t[names(coef(model_f_tr))]
robust_f_tr_t     <- robust_f_tr_t[names(coef(model_f_tr))]
nw_se_f_china_t  <- nw_se_f_china_t[names(coef(model_f_ch))]
robust_f_ch_t <- robust_f_ch_t[names(coef(model_f_ch))]


# list of models, SE and p-value
models_list_f <- list(model_f_d, model_f_n, model_f_ta, model_f_tr, model_f_ch)
robust_ses_f <- list(nw_se_f_d_t, nw_se_f_n_t, nw_se_f_ta_t, nw_se_f_tr_t, nw_se_f_china_t)
robust_pvals_f <- list(robust_f_d_t, robust_f_n_t, robust_f_ta_t, robust_f_tr_t, robust_f_ch_t)

# Name of coefficient
custom_names <- list(
  "vol.l1" = "$AHV_{t-1}$",
  "vol.l2" = "$AHV_{t-2}$",
  "vol.l3" = "$AHV_{t-3}$",
  "vol.l4" = "$AHV_{t-4}$",
  "vol.l5" = "$AHV_{t-5}$",
  "vol.l6" = "$AHV_{t-6}$",
  "X.l1" = "$X_{t-1}$",
  "X.l2" = "$X_{t-2}$",
  "X.l3" = "$X_{t-3}$",
  "X.l4" = "$X_{t-4}$",
  "X.l5" = "$X_{t-5}$",
  "X.l6" = "$X_{t-6}$",
  "const" = "Constant"
)

tmpfile_f <- tempfile(fileext = ".html")  # create temp file

# Generate table
table_texreg_f <- htmlreg(
  l = models_list_f,
  override.se = robust_ses_f,
  override.pvalues = robust_pvals_f,
  custom.model.names = c("TweetDummy", "TweetCount", "Tariff", "Trade", "China"),
  custom.coef.map = custom_names,
  caption = "First-Term VAR Models of Average Hourly Volatility",
  label = "tab:VAR_First_Term",
  caption.above = TRUE,
  digits = 6,
  custom.gof.rows = list("Shock (IRF)" = c(0.002919, 0.002236, 0.000484, 0.000702, 0.000904)),
  star.cutoffs = c(0.001, 0.01, 0.05),
  custom.note = "\\parbox[t]{0.9\\textwidth}{\\small\\textit{This table displays VAR regression with only two variables : AHV and X regressor. The column names represent the X variable for the selected model.}}",
  file = tmpfile_f
)

# Print table
cat(readLines(tmpfile_f), sep = "\n")

```

### VAR Third Table

```{r third_table, message=FALSE, warning=FALSE, results='asis', cache=TRUE}

#Second

d_s_d_t = d_s_d %>%
    rename(X.l1 = dummy.l1,
    X.l2 = dummy.l2,
    X.l3 = dummy.l3,
    X.l4 = dummy.l4,
    X.l5 = dummy.l5,
    X.l6 = dummy.l6)

f_t_s_d <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_s_d <- lm(f_t_s_d, data = d_s_d_t)


d_s_n_t = d_s_n %>%
    rename(X.l1 = N.l1,
    X.l2 = N.l2,
    X.l3 = N.l3,
    X.l4 = N.l4,
    X.l5 = N.l5,
    X.l6 = N.l6)

f_t_s_n <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_s_n <- lm(f_t_s_n, data = d_s_n_t)


d_s_ta_t = d_s_ta %>%
    rename(X.l1 = tariff.l1,
    X.l2 = tariff.l2,
    X.l3 = tariff.l3,
    X.l4 = tariff.l4,
    X.l5 = tariff.l5,
    X.l6 = tariff.l6)

f_t_s_ta <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_s_ta <- lm(f_t_s_ta, data = d_s_ta_t)


d_s_tr_t = d_s_tr %>%
    rename(X.l1 = trade.l1,
    X.l2 = trade.l2,
    X.l3 = trade.l3,
    X.l4 = trade.l4,
    X.l5 = trade.l5,
    X.l6 = trade.l6)


f_t_s_tr <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_s_tr <- lm(f_t_s_tr, data = d_s_tr_t)


d_s_ch_t = d_s_ch %>%
    rename(X.l1 = china.l1,
    X.l2 = china.l2,
    X.l3 = china.l3,
    X.l4 = china.l4,
    X.l5 = china.l5,
    X.l6 = china.l6)

f_t_s_ch <- as.formula("y ~ -1 + vol.l1 + vol.l2 + vol.l3 + vol.l4 + vol.l5 + vol.l6 +
                         X.l1 + X.l2 + X.l3 + X.l4 + X.l5 + X.l6 + const")
model_s_ch <- lm(f_t_s_ch, data = d_s_ch_t)


nw_se_s_d_t <- sqrt(diag(sandwich::NeweyWest(model_s_d, lag = 6)))
nw_se_s_n_t <- sqrt(diag(sandwich::NeweyWest(model_s_n, lag = 6)))
nw_se_s_ta_t <- sqrt(diag(sandwich::NeweyWest(model_s_ta, lag = 6)))
nw_se_s_tr_t <- sqrt(diag(sandwich::NeweyWest(model_s_tr, lag = 6)))
nw_se_s_china_t <- sqrt(diag(sandwich::NeweyWest(model_s_ch, lag = 6)))


robust_s_d_t <- 2 * (1-pt(abs(coef(model_s_d) / nw_se_s_d_t), df = df.residual(model_s_d)))
robust_s_n_t <- 2 * (1-pt(abs(coef(model_s_n) / nw_se_s_n_t), df = df.residual(model_s_n)))
robust_s_ta_t <- 2 * (1-pt(abs(coef(model_s_ta) / nw_se_s_ta_t), df = df.residual(model_s_ta)))
robust_s_tr_t <- 2 * (1-pt(abs(coef(model_s_tr) / nw_se_s_tr_t), df = df.residual(model_s_tr)))
robust_s_ch_t <- 2 * (1-pt(abs(coef(model_s_ch) / nw_se_s_china_t), df = df.residual(model_s_ch)))

nw_se_s_d_t       <- nw_se_s_d_t[names(coef(model_s_d))]
robust_s_d_t      <- robust_s_d_t[names(coef(model_s_d))]
nw_se_s_n_t      <- nw_se_s_n_t[names(coef(model_s_n))]
robust_s_n_t     <- robust_s_n_t[names(coef(model_s_n))]
nw_se_s_ta_t      <- nw_se_s_ta_t[names(coef(model_s_ta))]
robust_s_ta_t     <- robust_s_ta_t[names(coef(model_s_ta))]
nw_se_s_tr_t     <- nw_se_s_tr_t[names(coef(model_s_tr))]
robust_s_tr_t     <- robust_s_tr_t[names(coef(model_s_tr))]
nw_se_s_china_t  <- nw_se_s_china_t[names(coef(model_s_ch))]
robust_s_ch_t <- robust_s_ch_t[names(coef(model_s_ch))]

# lists of model, robust SE  and p-values 
models_list_s <- list(model_s_d, model_s_n, model_s_ta, model_s_tr, model_s_ch)
robust_ses_s <- list(nw_se_s_d_t, nw_se_s_n_t, nw_se_s_ta_t, nw_se_s_tr_t, nw_se_s_china_t)
robust_pvals_s <- list(robust_s_d_t, robust_s_n_t, robust_s_ta_t, robust_s_tr_t, robust_s_ch_t)

tmpfile_s <- tempfile(fileext = ".html")  # create temp file


# Generate table
table_texreg_s <- htmlreg(
  l = models_list_s,
  override.se = robust_ses_s,
  override.pvalues = robust_pvals_s,
  custom.model.names = c("TweetDummy", "TweetCount", "Tariff", "Trade", "China"),
  custom.coef.map = custom_names,
  caption = "Second-Term VAR Models of Average Hourly Volatility",
  label = "tab:VAR_Second_Term",
  caption.above = TRUE,
  digits = 6,
  custom.gof.rows = list("Shock (IRF)" = c(0.014659, 0.013315, 0.010752, -0.005665, 0.013937)),
  star.cutoffs = c(0.05, 0.01, 0.001),
  custom.note = "\\parbox[t]{0.9\\textwidth}{\\small\\textit{This table displays VAR regression with only two variables : AHV and X regressor. The column names represent the X variable for the selected model.}}",
  file = tmpfile_s
)

 
# Print
cat(readLines(tmpfile_s), sep = "\n")
```
