---
title: "ARMA-X Models"
output:
  html_document: 
---
\newpage

```{r library_setup, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
rm(list=ls())
require(tinytex) #LaTeX
require(ggplot2) #plots
require(AEC) #JP-Renne functions
require(AER) #NW formula
require(forecast) #time series stuff
require(expm) #matrix exponents
require(here) #directory finder
require(stringr) # analysis of strings, important for the detection in tweets
require(dplyr) #data management
require(lubridate) #data dates management
require(zoo) #for lagging
require(jtools) #tables
require(huxtable) #tables
require(lmtest) #reg tests
require(vroom) #for loading data
require(data.table) #for data filtering
require(sysid) #for ARMA-X modeling
require(sandwich) #regression errors
require(stargazer) #nice reg tables
require(tidytext) #text mining
require(textstem) #lemmatization
require(quanteda) #tokenization
require(texreg) #arima tables
require(future.apply) #parallel computation (speed)
require(aTSA) #adf test

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
source(here("helperfunctions/truths_cleaning_function.R"))
source(here("helperfunctions/armax_functions.R"))

```

```{r datasetup, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE}

#load final dataset
source(here("helperfunctions/full_data.R"))

#backup
backup = data
data = backup

#select timeframe 
data = filter(data,between(timestamp, as.Date('2014-01-01'), as.Date('2025-05-07')))

```


# Full Timeframe

## SPY Models
```{r SPYarmax, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$SPY_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$SPY_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$SPY_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$SPY_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$SPY_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$SPY_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$SPY_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```



## SPY IRFs
```{r SPYirf, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```


## SPY Residuals
```{r SPYresiduals, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

## VGK Models
```{r VGKarmax, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$VGK_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$VGK_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$VGK_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$VGK_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$VGK_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$VGK_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$VGK_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```


## VGK IRFs
```{r VGKirf, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## VGK Residuals
```{r VGKresiduals, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

## ASHR Models
```{r ASHRarmax, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$ASHR_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$ASHR_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$ASHR_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$ASHR_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$ASHR_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$ASHR_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$ASHR_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```

## ASHR IRFs
```{r ASHRirfs, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## ASHR Residuals
```{r ASHRresiduals, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

# First Term

```{r datasetup first, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE}

#load final dataset
data = backup

#first term
data = filter(data,between(timestamp, as.Date('2017-01-20'), as.Date('2021-01-20')))

```


## SPY Models
```{r SPYarmax first, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$SPY_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$SPY_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$SPY_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$SPY_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$SPY_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$SPY_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$SPY_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```

## SPY IRFs
```{r SPYirf first, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## SPY Residuals
```{r SPYresiduals first, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

## VGK Models
```{r VGKarmax first, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$VGK_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$VGK_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$VGK_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$VGK_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$VGK_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$VGK_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$VGK_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```

## VGK IRFs
```{r VGKirf first, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## VGK Residuals
```{r VGKresiduals first, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

## ASHR Models
```{r ASHRarmax first, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$ASHR_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$ASHR_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$ASHR_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$ASHR_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$ASHR_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$ASHR_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$ASHR_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```

## ASHR IRFs
```{r ASHRirfs first, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## ASHR Residuals
```{r ASHRresiduals first, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

# Second Term

```{r datasetup second, results=FALSE, warning=FALSE, message=FALSE, echo=FALSE}

#load final dataset
data = backup

#second term
data = filter(data,between(timestamp, as.Date('2025-01-20'), as.Date('2025-05-07')))

```



## SPY Models
```{r SPYarmax second, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$SPY_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$SPY_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$SPY_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$SPY_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$SPY_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$SPY_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$SPY_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```

## SPY IRFs
```{r SPYirf second, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## SPY Residuals
```{r SPYresiduals second, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

## VGK Models
```{r VGKarmax second, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$VGK_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$VGK_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$VGK_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$VGK_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$VGK_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$VGK_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$VGK_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```

## VGK IRFs
```{r VGKirf second, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## VGK Residuals
```{r VGKresiduals second, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```

\newpage

## ASHR Models
```{r ASHRarmax second, results="asis", warning=F, message=F}

#dummy
dummy_fit = auto.armax.r(data$ASHR_vol, x=data$dummy, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#count
count_fit = auto.armax.r(data$ASHR_vol, x=data$N, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#tariffs 
tariff_fit = auto.armax.r(data$ASHR_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#trade
trade_fit = auto.armax.r(data$ASHR_vol, x=data$trade, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#china
china_fit = auto.armax.r(data$ASHR_vol, x=data$china, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of positive
positive_fit = auto.armax.r(data$ASHR_vol, x=data$prop_positive, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

#proportion of negative
negative_fit = auto.armax.r(data$ASHR_vol, x=data$prop_negative, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)

```

## ASHR IRFs
```{r ASHRirfs second, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 15

irf.plot(dummy_fit$model,nb.periods)
irf.plot(count_fit$model,nb.periods)
irf.plot(tariff_fit$model,nb.periods)
irf.plot(trade_fit$model,nb.periods)
irf.plot(china_fit$model,nb.periods)
irf.plot(positive_fit$model,nb.periods)
irf.plot(negative_fit$model,nb.periods)

```

## ASHR Residuals
```{r ASHRresiduals second, warning=F, message=F}

res = checkresiduals(dummy_fit$model, plot = FALSE)
res = checkresiduals(count_fit$model, plot = FALSE)
res = checkresiduals(tariff_fit$model, plot = FALSE)
res = checkresiduals(trade_fit$model, plot = FALSE)
res = checkresiduals(china_fit$model, plot = FALSE)
res = checkresiduals(positive_fit$model, plot = FALSE)
res = checkresiduals(negative_fit$model, plot = FALSE)


```















































