---
title: "ARMA-X Analysis Tutorial"
output:
  pdf_document: 
    toc: true
    fig_caption: yes
    latex_engine: lualatex
header-includes:
  - \usepackage{amsmath}
---
\newpage

# Setup

## Load Libraries \& Functions
```{r library_setup, results=FALSE, warning=FALSE, message=FALSE}
rm(list=ls())
require(tinytex) #LaTeX
require(ggplot2) #plots
require(AEC) #JP-Renne functions
require(AER) #NW formula
require(forecast) #time series stuff
require(expm) #matrix exponents
require(here) #directory finder
require(stringr) # analysis of strings, important for the detection in tweets
require(dplyr) #data management
require(lubridate) #data dates management
require(zoo) #for lagging
require(jtools) #tables
require(huxtable) #tables
require(lmtest) #reg tests
require(vroom) #for loading data
require(data.table) #for data filtering
require(sysid) #for ARMA-X modeling
require(sandwich) #regression errors
require(stargazer) #nice reg tables
require(tidytext) #text mining
require(textstem) #lemmatization
require(quanteda) #tokenization
require(texreg) #arima tables
require(future.apply) #parallel computation (speed)
require(aTSA) #adf test

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
source(here("helperfunctions/truths_cleaning_function.R"))
source(here("helperfunctions/armax_functions.R"))

```


## Load Data 

Use the full_data script to load our final dataset. Then select the 
timeframe.
```{r datasetup, results=FALSE, warning=FALSE, message=FALSE}

#load final dataset
source(here("helperfunctions/full_data.R"))

#select timeframe 
data = filter(data,between(timestamp, as.Date('2014-01-01'), as.Date('2025-05-07')))

#first term
#data = filter(data,between(timestamp, as.Date('2017-01-20'), as.Date('2021-01-20')))

#second term
#data = filter(data,between(timestamp, as.Date('2025-01-20'), as.Date('2025-05-07')))

```


# Stationarity
Having a p.value of 0.01 for our main variables seems to indicate stationarity.
```{r adf tests, message=FALSE, warning=FALSE, results=FALSE}

adf.test(data$SPY_vol)
adf.test(data$VGK_vol)
adf.test(data$ASHR_vol)

adf.test(data$N)
adf.test(data$tariff)
adf.test(data$china)

```
\newpage

# Univariate ARMA-X Models

## Custom ARMA-X Specification

This first function allows to run a certain specification of an ARMA-X model.
We needed to create this function due to the creation of the lags for the 
exogenous regressor. 
```{r armax function, results="asis", warning=F, message=F}
#armax enables a custom armax specification with p,q,r 
res2 = armax(data$SPY_vol, xreg=data$tariff, nb.lags=2,
                   p=5, q=0, d=0, latex=T)
```

## Best ARMA-X Given r

This second function uses the base auto.arima function in order to look for the
best (lowest AIC) specification given a certain number of x lags. Once again
it was necessary to create a custom function for this due to the creation of 
the lags for the exogenous regressor.
```{r autoarmax function, results="asis", warning=F, message=F}

#auto.armax selects the lowest AIC value given r (exogenous variable lags) 
res1 = auto.armax(data$SPY_vol,xreg=data$tariff,nb.lags=2,
                latex=T,max.p = 6, max.q = 6, max.d=0)
```


## Best ARMA-X

This third function is the most sophisticated. We've had to essentially custom
code the auto.arima function in order to loop for p, q and r. It also
provides many useful details such as a plot of the AIC value for the different 
number of lags. Note that the output of this function is a list, so in order get 
the model output, it is needed to specifically call it (see how the call works
for this third model in the IRF section). The latex option in all functions 
determines whether the output is console-friendly, or output-friendly.
```{r autoarmax with r function, results="asis", warning=F, message=F}
#auto.armax.r selects the lowest AIC checking all 3 p,q,r values
res3 = auto.armax.r(data$SPY_vol, x=data$tariff, 
                max_p = 3, max_q = 3, max_r = 3, criterion = "AIC", latex=T)
```


## IRF

Finally, we have our personal twist on the IRF plot function from the AEC package.
It enables automatic extraction of the phi's and beta's of a fitted ARMA-X model.
It then uses the provided sim.arma function where it inputs the beta's as theta's.
Finally, it automatically plots it, using a fancy ggplot.
```{r irf, results="asis", warning=F, message=F}

#we want to plot the IRFs of these models
nb.periods = 7 * 20
irf.plot(res1,nb.periods)
irf.plot(res2,nb.periods)
irf.plot(res3$model,nb.periods)

```




















