---
title: "Financial Data Analysis Tutorial"
output:
  pdf_document: 
    toc: true
    fig_caption: yes
    latex_engine: lualatex
header-includes:
  - \usepackage{amsmath}
---
\newpage

# Setup

## We load the required libraries
```{r library_setup, results=FALSE, warning=FALSE, message=FALSE}
rm(list=ls())
require(tinytex) #LaTeX
require(ggplot2) #plots
require(AEC) #JP-Renne functions
require(forecast) #time series stuff
require(expm) #matrix exponents
require(here) #directory finder
require(stringr) # analysis of strings, important for the detection in tweets
require(dplyr) #data management
require(lubridate) #data dates management
require(zoo) #for lagging
require(jtools) #tables
require(huxtable) #tables
require(lmtest) #reg tests
require(vroom) #for loading data

getwd()
#setwd("...") -> set wd at base repo folder

#load helper functions
source(here("helperfunctions/data_loaders.R"))
source(here("helperfunctions/date_selector.R"))
source(here("helperfunctions/plotters.R"))
source(here("helperfunctions/quick_arma.R"))
source(here("helperfunctions/r.vol_calculators.R"))
```

\newpage

# Data
Note that this document uses intermediate data to show how we produce the financial
part of the final data. It also shows various functions we developed to 
implement some quick analysis and plotting.


## Raw Data
Use our custom data loading function as our financial data is fractured by month
due to the downloading constraints.
```{r rawdata_setup, results=FALSE, warning=FALSE, message=FALSE}

#market prices (loads and names them automatically)

#S&P500
data_loader(symbol="SPY")

#STOXX50
data_loader(symbol="VGK")

#CSI 300 (China)
data_loader(symbol="ASHR")

```

\newpage

# Quick Analysis

## SPY April 2nd 2025
Here are some functions we developed in order to be able to easily select certain
dates for our financial data. Comes in handy for our plotter functions as well 
as later in the calculation of the realised volatility.
```{r helper tutorial, warning=FALSE, message=FALSE}

#extract a particular day
SPY_25_04_02 = day_selector(raw_SPY,2025,04,02) #april 2nd 2025

#let's plot it
price_plotter_day(SPY_25_04_02,"SPY Price on April 2nd 2025") 

#quickly test some ARMA specifications
quick_arma(SPY_25_04_02,1,0,0) #checking AR1,AR2,AR3
#quick_arma(SPY_25_04_02,2,0,0) #checking AR2,AR3,AR4


#extract a particular month
SPY_24_09 = month_selector(raw_SPY,2024,09) #november 2024


#extract a particular year
SPY_24 = year_selector(raw_SPY,2024) #2024

```

\newpage

# Realised Volatility

## Computations
We have developed several functions for the computation of realised volatility.
The only areas where they differ is in the timeframe of the input dataset, and 
whether it calculates the daily average or the hourly average. Note that we
use hourly data in our final analysis. \
These functions can be found in the helperfunctions folder.
```{r volatility compute, warning=FALSE, message=FALSE}

#avg per day for each month of any dataset
vol_SPY_daily = r.vol_daily(raw_SPY,merge=F)
head(vol_SPY_daily)

#can then filter out years, months, or days
vol_24d = year_selector(vol_SPY_daily,2024)
vol_24_08d = month_selector(vol_SPY_daily,2024,08)
vol_24_11_04d = day_selector(vol_SPY_daily,2024,11,04) #scalar


#avg per hour for each day of each month of any dataset
vol_SPY_hourly = r.vol_hourly(raw_SPY,merge=F)
head(vol_SPY_hourly)

#can then filter out years, months, or days
vol_24h = year_selector(vol_SPY_hourly,2024)
vol_24_08h = month_selector(vol_SPY_hourly,2024,08)
vol_24_11_04h = day_selector(vol_SPY_hourly,2024,11,04) #vector

```


## Plots
We have developed two functions in order to easily plot our volatility data 
in nice ggplots. One is for the daily average and the other for the hourly average.
```{r volatility plots, warning=FALSE, message=FALSE}

#avg per day volatility all time
dvol_plotter(vol_SPY_daily,breaks="yearly",
             title="Realised Volatility - SPY")


#hourly volatility all time
hvol_plotter(vol_SPY_hourly,breaks="yearly",
             title="Realised Volatility - SPY")

```








